\documentclass{beamer}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{quotes, angles}
\usepackage{graphicx}
\usepackage{multicol}
%\usepackage{pgfplots}
%\pgfplotsset{width=10cm,compat=1.9}
%\usepackage{pgfplotstable}

\setlength{\headheight}{26pt}%doesn't seem to fix warning

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

%\rhead{\small{24 March 2019}}
\lhead{\small{BECA / Dr. Huson / Geometry - Course Plans}}

\renewcommand{\headrulewidth}{0pt}

\title{10th Grade Geometry - Rules \& Practices}
\subtitle{Bronx Early College Academy}
\author{Christopher J. Huson PhD}
\date{26 June 2019}

\begin{document}
\frame{\titlepage}
\section[Outline]{}
\frame{\tableofcontents}


\section{0.1 Handouts}
  \frame
  {
    \frametitle{GQ: What rules and practices do students follow?}
    \framesubtitle{CCSS: HSG.CO.D.12 Congruence, geometric constructions \hfill \alert{13.1 Tuesday 28 May}}

    \begin{block}{Handouts}
      \begin{enumerate}
        \item Syllabus
        \item Materials requirements, checklist
      \end{enumerate}
    \end{block}
    Habits for success\\[0.25cm]
    Turn in homework, sit in assigned seat, notebook \& materials out, begin Do Now.
  }

\section{0.2 Notebook, note taking}
  \frame
  {
    \frametitle{GQ: How do we use a notebook to support our memory?}
    \framesubtitle{IB trait: Reflection \hfill \alert{0.1 Thursday 11 Sept}}

    \begin{block}{Composition notebook \\(should be out during class, except tests)}
      \begin{enumerate}
        \item Record information
        \item Summarize key ideas
        \item Save examples
        \item Should not include practice work (use scrap paper)
      \end{enumerate}
    \end{block}
    It must have your name on the front\\[0.25cm]
    On first page, write the following: your name, the course, my name, my phone \& email. \\(Geometry / Dr. Huson / 917-648-5632 / husonbeca@gmail.com)
  }

\section{0.2 Folder, scrap paper, homework}
  \frame
  {
    \frametitle{GQ: How do we learn mathematics?}
    \framesubtitle{IB trait: Reflection \hfill \alert{0.1 Thursday 11 Sept}}

    \begin{block}{Practice communicating mathematics in writing}
      \begin{enumerate}
        \item Have plenty of scrap paper available: lined, blank, graph
        \item Learn to use tools efficiently: pencil, pen, ruler, compass, tape measure
        \item Turn in work in the bin
        \item Carry papers in a \emph{math folder}
        \item Throw away old papers regularly
      \end{enumerate}
    \end{block}
    Write your (last) name on the top right front of every page\\[0.25cm]
    Use MLA-formatted header as appropriate (name / course / my name / date / assignment title)
  }

\section{0.2 Portfolio binder}
  \frame
  {
    \frametitle{GQ: How do we show the results of a year's work?}
    \framesubtitle{IB trait: Reflection \hfill \alert{0.1 Thursday 11 Sept}}

    \begin{block}{Portfolio binder}
      \begin{enumerate}
        \item Constructions (final copy, not practice on scrap paper)
        \item Quizzes and tests, test reflections, \& corrections
        \item Projects
      \end{enumerate}
    \end{block}
    Binder stays in the classroom\\[0.25cm]
    It must have your name on the spine and may be decorated
  }

\section{0.3 Test corrections}
  \frame
  {
    \frametitle{GQ: How do we learn from test results?}
    \framesubtitle{IB trait: Reflection \hfill \alert{0.1 Thursday 11 Sept}}

    \begin{block}{Handouts}
      \begin{enumerate}
        \item Study for tests
        \item After test, review problems in class. Complete reflection form
        \item Work test corrections at lunch, gain half of lost test points
      \end{enumerate}
    \end{block}
    Habits for success\\[0.25cm]
    Turn in homework, sit in assigned seat, notebook \& materials out, begin Do Now.
  }

\section{13.4 Constructions, Similarity quiz Friday 31 May}
  \frame
  {

  }

  \section{13.5 Slope review Wednesday 5 June}
    \frame
    {

    }

    \frame
    {

      }

  \section{13.6 Similarity review Friday 7 June}
    \frame
    {

    }

\end{document}
