\documentclass[12pt, twoside]{article}
\usepackage[letterpaper, margin=1in, headsep=0.5in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{quotes, angles}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{venndiagram}

\newif\ifmeta
\metatrue %print standards and topics tags

\title{IB Mathematics}
\author{Chris Huson}
\date{September 2021}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % disable the underline of the header
\raggedbottom


\fancyhead[LE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{4cm} \,\\}
\fancyhead[LO]{BECA / IB Math 01-Linear functions\\* 8 October 2021}

\begin{document}

\subsubsection*{Quiz: I can model with linear functions}

\begin{enumerate}[itemsep=0.75cm]
  \item Solve for $x$
  \begin{multicols}{2}
    \begin{enumerate}[itemsep=3cm]
      \item $3x-7=-4$
      \item $\frac{3}{5}x =30$
      \item $2(x+5)=12$
      \item $\frac{2}{3}(x+7)=x-4$
    \end{enumerate}
  \end{multicols} \vspace{3cm}

  \item The perimeter of a rectangle is 54 centimeters. If its length is 6 cm., what is its width? \vspace{3cm}
  
  \item Round to the \emph{nearest hundredth}: 9.7549
  \item Round to the \emph{nearest tenth}: 10.974
  \item Round to the \emph{nearest thousand}: 147,321.94

  \item Express as a number: $1.27 \times 10^4$
  \item Express as a number: $3.3 \times 10^{-2}$
  \item Express in scientific notation: $47,200$
  
  \newpage
  \item Simplify each of these expressions employing absolute value.
  \begin{multicols}{2}
    \begin{enumerate}[itemsep=1.7cm]
      \item $|-7|$
      \item $|2-5|$
      \item $|-3+2|$
      \item $|-4|-|7|$
    \end{enumerate}
  \end{multicols}

  \item Use a calculator to simplify each expression to a decimal.
  \begin{multicols}{2}
  \begin{enumerate}[itemsep=1.5cm]
    \item $3.4 \times 9.8 \times 4.3 \times 0.15$ 
    \item $13.65 + \frac{1}{2} (8.6)$  
    \item $12 + \frac{1}{4} \sqrt{12}$
    \item $\frac{1}{3} \pi (3.4)^2(6.1)$
  \end{enumerate}
  \end{multicols}\vspace{0.5cm}

  \item Simplify each of the following to a fraction.
  \begin{multicols}{2}
  \begin{enumerate}[itemsep=4cm]
    \item $\displaystyle 2+\frac{3}{5}-\frac{1}{4}$ 
    \item $\displaystyle \frac{1}{4} \times \frac{3}{2} + \frac{5}{2} \times \frac{1}{4}$
  \end{enumerate}
  \end{multicols}\vspace{3cm}

\item Simplify each radical. (do not convert to a decimal)
  \begin{multicols}{2}
    \begin{enumerate}[itemsep=2cm]
      \item $\sqrt{50}$ 
      \item $2\sqrt{3} - \sqrt{3}$
      \item $\sqrt{27}$ 
      \item $\displaystyle \frac{\sqrt{18}}{\sqrt{2}}$ 
    \end{enumerate}
    \end{multicols}\vspace{2cm}
  
\newpage
\item Solve for each system of equations for $x$ and $y$.
\begin{multicols}{2}
  \begin{enumerate}
    \item $2x+y=7$ \\
    $x -y =-1$
    \item $x-3y=-2$ \\
    $2x+y =31$
  \end{enumerate}
\end{multicols} \vspace{7cm}

\item Roll a regular, six-sided die. What is the probability of rolling an even number?
\vspace{1cm}
\item Two coins are flipped. What is the probability of getting one heads and one tails?
\vspace{1cm}
\item Using the metric system, what would be the most natural units of measure for each quantities of an automobile.
\begin{enumerate}[itemsep=1cm]
  \item Its weight
  \item The capacity of the gas tank
  \item The length of the car overall
  \item Its top speed
\end{enumerate}
    
\newpage
\item Given the following data, find each summary statistic: ${7, 7, 9, 13, 17}$
\begin{enumerate}[itemsep=1cm]
  \item The mean
  \item The median
  \item The mode
  \item The range
\end{enumerate}

\item Given the following two sets:\\ $A=\{1,3,5,7\}$\\
$B=\{0,1,7,9\}$
\begin{enumerate}[itemsep=1cm]
  \item Find $A \cap B$\\*[20pt]
  \item Find $A \cup B$\\*[20pt]
  \item Place the elements of $A$ and $B$ in the appropriate regions in the Venn diagram below.
  \begin{center}
  \begin{venndiagram2sets}[tikzoptions={scale=1.5}]
  \end{venndiagram2sets}
\end{center}
\end{enumerate}

\end{enumerate}
\end{document}