\documentclass[12pt, twoside]{article}
\input{../preamble}
\usepackage{float}

\title{Algebra 2}
\author{Chris Huson}
\date{February 2024}

\fancyhead[RO]{\\ Name: \hspace{1.5cm} \,\\}
\fancyhead[LO]{BECA/Huson/Algebra 2: Complex Numbers \& Rational Exponents \\* 9 February 2024}

\begin{document}

\subsubsection*{3.8 Quiz: Working with exponents \hfill A.SSE.3c Exponent properties}
\emph{Do Not Use a Calculator}
\begin{enumerate}
\item Select all of the solutions to $x^2=36$.
    \begin{multicols}{2}
    \begin{enumerate}
        \item $x=4 \times 9$
        \item $x=2 \times 18$
        \item $x=6$
        \item $x=-6$
        \item $x=18$
        \item $x=-18$
    \end{enumerate}
    \end{multicols}

    \item Find the value of each variable that makes the equation true.
    \begin{multicols}{2}
    \begin{enumerate}[itemsep=0.5cm]
        \item $\displaystyle \frac{5^9}{5^5} = 5^b \hspace{1.4cm}  a=$
        \item $11^c=1 \hspace{1.4cm} b=$
        \item $(2^3)^4 = 2^d \qquad c=$
        \item $\displaystyle 3^e = \frac{1}{9} \hspace{1.6cm}  d=$
        \item $7^5 \cdot 7^2 = 7^a \qquad e=$
        \item $4^5 \cdot f^5 = 8^5 \qquad f=$
    \end{enumerate}
    \end{multicols} \vspace{0.5cm}

\item Evaluate each expression.
    \begin{multicols}{2}
    \begin{enumerate}[itemsep=0.5cm]
        \item $\displaystyle \frac{1}{5} \cdot 30=$
        \item $\displaystyle \frac{5}{6} \cdot 12=$
        \item $\displaystyle \frac{4}{7} \cdot 12 \cdot \frac{7}{4}=$
        \item $\displaystyle \frac{3}{5} \cdot \frac{7}{3} \cdot 10=$
    \end{enumerate}
    \end{multicols} \vspace{0.5cm}

\item $s = 2x - 1 $ and $t = 5x + 7$. \hfill (AI-A.APR.1 Add, subtract, \& multiply polynomials) \\[0.5cm]
For each expression, write an equivalent expression and simplify.
    \begin{enumerate}[itemsep=0.75cm]
        \item $s+t =$
        \item $s-t =$
        \item $st =$
    \end{enumerate}

\newpage
\subsubsection*{A2-F.BF.2 Write arithmetic and geometric sequences with recursive formulas}
\item Given the geometric sequence beginning $a_1 = 9$, $a_2 = 3$, $a_3 = 1$, $a_4 = \frac{1}{3}, \ldots$      
    \begin{enumerate}[itemsep=2cm]
        \item Write a recursive definition of the sequence.
        \item Write a formula expression of the sum of the first 10 terms of the sequence. (You do not need to calculate the sum's value.)
    \end{enumerate}
    \vspace{2cm}

\item Given the function $f(x)=(3x+10)(x+1)(x-2)$. \hfill (AII-F.IF.7c Graph polynomials)
    \begin{center}
    \begin{tikzpicture}[xscale=0.7, yscale=0.7]
        \draw [thick, ->] (-7.2,0) -- (7.5,0) node [above] {$x$};
        \draw [thick, ->] (0,-6.2)--(0,7.5) node [right] {$y$};
        %\foreach \x in {-7,...,7} \draw (\x cm,5pt) -- (\x cm,-5pt);
    \end{tikzpicture}
    \end{center}
    \begin{enumerate}
        \item Sketch a graph of the function.
        \item Mark and label all $x$-intercepts of the graph.
        \item Calculate the function's $y$-intercept and mark it on the graph.
    \end{enumerate}


\end{enumerate}
\end{document}