\documentclass{beamer}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{quotes, angles}
\usepackage{graphicx}
\usepackage{multicol}

%\usepackage{pgfplots}
%\pgfplotsset{width=10cm,compat=1.9}
%\usepackage{pgfplotstable}

\setlength{\headheight}{26pt}%doesn't seem to fix warning

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

%\rhead{\small{3 September 2019}}
\lhead{\small{BECA / Dr. Huson / Geometry Unit 1}}

\renewcommand{\headrulewidth}{0pt}

\title{Mathematics Class Slides}
\subtitle{Bronx Early College Academy}
\author{Christopher J. Huson PhD}
\date{21-25 September 2020}

\begin{document}
\frame{\titlepage}
\section[Outline]{}
\frame{\tableofcontents}

\section{1.3 Equilateral triangle construction, 25, 29 Sept}
\frame
{
  \frametitle{GQ: How do we construct an equilateral triangle?}
  \framesubtitle{CCSS: HSG.CO.D.13 Construct an equilateral triangle \hfill \alert{1.3 Friday 25, 29 Sept}}

  \begin{block}{Do Now: $x=0$ vs $y=0$. Copy into notebook, do problems}
  \begin{enumerate}
      \item $x=0$, starting point, $y$-intercept, $b$, initial condition, $f(0)$
      \item $y=0$, $x$-intercept, the solution, the zeros, $f(x)=0$
  \end{enumerate}
  \end{block}
  Lesson: Circle notation; ``Sketch", ``draw", ``construct"; ``Given"\\[5pt]
  Euclid's first construction
  \begin{enumerate}
      \item Steps in the construction
      \item Logic: Why does it work?
      \item MLA headings: First+Last Name / Dr. Huson \\
      10.x Geometry / 9 September 2019
      \item Assessment criteria: precision, correct \& complete, elegance
  \end{enumerate}
  Homework: Measurement, terminology, and algebra practice\\
  Due: Compass, ruler, protractor, calculator
}

\section{1.5 Angle terminology, 11 Sept}
  \frame
  {
    \frametitle{GQ: How do we measure angles?}
    \framesubtitle{CCSS: HSG.CO.A.1 Know precise geometric definitions \hfill \alert{1.5 Wednesday 11 Sept}}
 
    \begin{block}{Do Now: How big is a football field?}
      \begin{enumerate}
          \item On lined scrap paper, calculate the area of a football field
          \item 100 yards long, $53 \frac{1}{3}$ yards wide
          \item What is the area of the end zone? (10 yards deep)
          \item Spicy: What is the area in square feet?
      \end{enumerate}
      \end{block}
    Lesson: Measuring angles, making angles of a given measure\\
    Angle terminology: legs, vertex, interior, exterior, right, acute, obtuse; adjacent, opposite or vertical angles\\ \vspace{0.5cm}
    Homework: Pretest handout, \alert{Test Friday}
  }
    
\section{1.6 Angle terminology, quiz review, 12 Sept}
\frame
{
  \frametitle{GQ: How do we measure angles?}
  \framesubtitle{CCSS: HSG.CO.A.1 Know precise geometric definitions \hfill \alert{1.6 Thursday 12 Sept}}
  \begin{block}{Do Now handout}
  \begin{enumerate}
      \item Measuring angles
      \item Protractor use
      \item Making angles of a given measure
  \end{enumerate}
  \end{block}
  Angle terminology: legs, vertex, interior, exterior, right, acute, obtuse\\
  Review for \alert{test tomorrow} \\
  Homework: Study for test
}

\end{document}