\documentclass{beamer}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{venndiagram}

%\usepackage{pgfplots}
%\pgfplotsset{width=10cm,compat=1.9}
%\usepackage{pgfplotstable}

\setlength{\headheight}{26pt}%doesn't seem to fix warning

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

%\rhead{\small{21 May 2018}}
\lhead{\small{BECA / Dr. Huson / Mathematics}}

%\vspace{1cm}

\renewcommand{\headrulewidth}{0pt}


\title{Mathematics Class Slides}
\subtitle{Bronx Early College Academy}
\author{Chris Huson}
\date{28 August 2018}

\begin{document}

\frame{\titlepage}


 \frame
 {
   \frametitle{Standard conventions for mathematical notation}
   \framesubtitle{Practice writing mathematics according to IB requirements, as per exam rubrics.}
 \begin{enumerate}
     \item Use the formula sheet.
     \item Chose the appropriate formula (M1).\\*
     (you do not have to copy the formula)
     \item Substitute values correctly (A1).
     \item Solve, showing key steps (A1).\\
     (skip routine algebra if you like)
     \item Write down the exact solution or copy the calculator display. An ellipsis (\ldots) indicates more digits (A1).
     \item Round to 3 significant digits (use $\approx$)(A1).
 \end{enumerate}
 }

 \frame
 {
   \frametitle{Standard conventions for mathematical notation}
   \framesubtitle{Practice writing mathematics according to IB requirements, as per exam rubrics.}
 Examples of key algebraic techniques
 \begin{enumerate}
     \item Setting a quadratic function $=0$
     \item Converting an exponent to a log
     \item Reading a value from a graph
     \item When writing lists, you may write only the first two and the last terms. For example,
 \[\sum_{k=1}^5 3 \cdot 2.25^k =3 + 6.75+\ldots+76.8867\ldots\]
 \[=135.99609\ldots \approx 136\]
 \end{enumerate}
 }

 \frame
 {
   \frametitle{Topics to cover in Reciprocals paper}
   \framesubtitle{Practice writing mathematics according to IB requirements, as per IA criteria.}
 \begin{enumerate}
 \item Asymptotic behavior explained with an example of end behavior.
 \item Translation of an example point ($A \xrightarrow{} A'$)
 \item Translation's impact on asymptotes.
 \item General case of horizontal and vertical translation. Use $h$ and $k$, and vector notation: $\begin{pmatrix} h \\ k \end{pmatrix}$
 \item Define a function and its inverse as a composition resulting in the identity. $(f \circ f^{-1})(x)=x$. Include an example.
 \item Inverse explained with an example point under reflection across $y=x$
 \item Discussion of reversal of the position of $h$ and $k$ in the algebraic representation of the function and its inverse. (perhaps with just example values)
 \end{enumerate}
 }


 \frame
 {
   \frametitle{Aim and rationale}
   \framesubtitle{There are many important and amazing sequences and series in mathematics.}
   $\displaystyle \frac{1}{2}+\frac{1}{4}+\frac{1}{8}+\frac{1}{16}+\frac{1}{32}+\frac{1}{64} \dots$ Zeno's paradox (Greek)\\*[10pt]  $\displaystyle \frac{1}{2}+\frac{1}{3}+\frac{1}{4}+\frac{1}{5}+\frac{1}{6}+\frac{1}{7} \dots$ harmonic series\\*[10pt]
   $\displaystyle \frac{\pi}{4}=1-\frac{1}{3}+\frac{1}{5}-\frac{1}{7}+\frac{1}{9}-\frac{1}{11}+\frac{1}{13}$ \dots Madhava  (India)\\*[10pt]
   %1, 1, 2, 3, 5, 8, 13, 21, 34, 55, 89,... (Fibonacci)\\*[10pt]
   0.99999999...\\*[10pt]
 The aim of this exploration is to discover the patterns, formulas, and rules of geometric series by experimenting and investigating using a spreadsheet to total various example series.\\*[5pt]

 *Sequence: list of numbers. Series: sum of a sequence of numbers. Geometric sequence: consecutive terms have a constant ratio.
 }

"How many subsets can be picked from a group of four students?"

 \end{document}
