\documentclass{beamer}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{venndiagram}

%\usepackage{pgfplots}
%\pgfplotsset{width=10cm,compat=1.9}
%\usepackage{pgfplotstable}

\setlength{\headheight}{26pt}%doesn't seem to fix warning

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

%\rhead{\small{21 May 2018}}
\lhead{\small{BECA / Dr. Huson / Mathematics}}

%\vspace{1cm}

\renewcommand{\headrulewidth}{0pt}


\title{Mathematics Class Slides}
\subtitle{Bronx Early College Academy}
\author{Chris Huson}
\date{28 August 2018}

\begin{document}

\frame{\titlepage}

\frame
{
  \frametitle{Extra help}
  framesubtitle{I am available to help with math questions}
\begin{itemize}
      \item Ask for a lunch pass to get help or do homework (no socializing)
      \item Work on your papers using the computers and printer in Room 414
      \item I can sometimes stay after school but ask ahead of time
\end{itemize}
 }

  \begin{frame}{Technical writing}
      \framesubtitle{Write a short paper answering a specific question}
      \begin{enumerate}
          \item Logical, step-by-step explanation, using an example
          \item Precise terminology, succinct:
          \item Notation: algebra symbols, tables, trees, grids
          \item Summary, big-picture, conceptual idea
          \item Audience: student peers
      \end{enumerate}
  \end{frame}

 \frame
 {
   \frametitle{Steps for writing technical papers}
   \framesubtitle{Practice writing mathematics according to IB requirements, as per IA criteria.}
 Proposal
 \begin{enumerate}
     \item Define an ``aim," including success criteria.
     \item Outline paper, especially Method including data collection, graphs, formulas; list references
     \item Draft introduction, including rationale and aim.
     \item Structure data tables, sketch graphs, begin formula and algebra (all handwritten, perhaps spreadsheets or Desmos)
     \item Draft Method section text
 \end{enumerate}
 Method
 \begin{enumerate}
     \item Collect data (survey, search, simulation, etc.)
     \item Work interactively with spreadsheets, graphing software, math
     \item Refine Method section, draft results and discussion.
 \end{enumerate}
 Complete mathematics and paper. Proofread carefully. Rewrite. Receive peer feedback. Rewrite. Submit final draft.
 }

 \frame
 {
   \frametitle{Standards for writing technical papers}
   \framesubtitle{Practice writing mathematics according to IB requirements, as per IA criteria.}
 Criterion C: Personal engagement (0-4 points)
 \begin{enumerate}
     \item Address a personal interest; ``make it your own"
     \item Think independently and/or creatively
     \item Present mathematical ideas in your own way
 \end{enumerate}
 Criterion D: Reflection (0-3 points)
 \begin{enumerate}
     \item Review, analyze, and evaluate the mathematics throughout the paper. Go beyond just describing results
     \item Link to the aims, comment on what has been learned, consider limitations, and compare different mathematical approaches
     \item Consider what's next, discuss the implications of results, strengths and weaknesses of approaches, and consider different perspectives
 \end{enumerate}
 }

 \frame
 {
   \frametitle{Communication protocols}
   \framesubtitle{How to send information and common conventions to follow}
 \begin{itemize}
       \item Mail (``post"), by messenger: formal, fancy, legally secure
       \item Text (cell phone): brief, informal, immediate, transitory
       \item Email: versatile, threaded, transitory or permanent (insecure)\\
       Subject line, salutations, handle@domain
       \item Attachments: .pdf is universally readable, can't be edited\\
       Microsoft Word, Excel, .ppt can be edited, commented
       \item Link: extended collaboration, commercial paywalls\\
       \emph{If you are not paying for it, you're not the customer; you're the product being sold.}
 \end{itemize}
  }

\end{document}
