\documentclass[12pt, oneside]{article}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Name: \hspace{1.5in} }
\lhead{BECA / Dr. Huson / Algebra 2 \\* 17 January 2018 \\* Classwork: Regents exponents problems}

\vspace{1cm}

\renewcommand{\headrulewidth}{0pt}

\title{Worksheet and test template}
\author{Chris Huson}
\date{January 2018}

\begin{document}

\subsubsection*{\\* Answer on lined paper. Show work.}

\begin{enumerate}

\vspace{0.5 cm}

\subsection*{Rational exponents and radicals}

\item Simplify $\sqrt[3]{x} \cdot \sqrt[3]{x} \cdot \sqrt[3]{x}$ 
\item Write $\sqrt[6]{x} \cdot \sqrt{x}$ as a single term with a rational exponent.

\item True of false:  $\displaystyle \big( 27^\frac{2}{9} \big) $ can be written as the equivalent radical expression $\sqrt[3]9$

\item For $x \neq 0$, which expressions are equivalent to one divided by the sixth root of $x$?
\[ \text{I. } \frac{\sqrt[6]{x}}{\sqrt[3]{x}} \text{  II. } \frac{x^{\frac{1}{6}}}{x^{\frac{1}{3}}} \text{  III. } x^{-\frac{1}{6}} \]

\subsection*{Polynomial algebra procedures}
\item Simplify $(x-3)(x+3)$
\item Simplify $(x-3)(-2x^2+5x+1)$
\item Evaluate $f(x)=x^2-2$ when $x=3$
\item Is 3 a zero of the function $f(x)=x^3-2x-20$?

\item Given $r(x)=x^3-4x^2+4x-6$, find the value of $r(2)$.\\*
What does your answer tell you about $x-2$ as a factor of $r(x)$? Explain.

\item A manufacturing company has developed a cost model,\\* $C(x)=0.15x^3 +0.01x^2+2x+120$, where $x$ is the number of items sold, in thousands. The sales price can be modeled by $S(x)=30-0.01x$. Therefore, revenue is modeled by $R(x)=x \cdot S(x)$.\\*[12pt]
The company’s profit, $P(x)=R(x)-C(x)$, could be modeled by what polynomial?

\subsection*{Graphing calculator solutions}
\item Given $f(x) = 3|x|-1$ and $g(x)=5$. Graph the two functions and make a quick sketch. Find the two solutions for the equation $f(x)=g(x)$, stating them as ordered pairs.

\subsection*{Logarithms}
\item What is the $\log_3{27}$?
\item Simplify $\ln{18}-\ln{2}$

\subsection*{Imaginary numbers}
\item Simplify $9i+(2i)^3$
\item Use the quadratic formula to find the solution to the equation $4x^2+98=0$.
\item The expression $6xi^3(-4xi + 5)$ is equivalent to...

\subsection*{Exponential functions}

\item Given the exponential function $\displaystyle f(x)=8.2e^{(0.47x)}$.
\begin{enumerate}
    \item Write down $f(0)$.\\*[25pt]
    \item Find $f(2)$.\\*[25pt]
    \item Solve for $x$ such that $f(x)=19$.\\*[95pt]
\end{enumerate}

\end{enumerate}
\end{document}