\documentclass[12pt, twoside]{article}
\usepackage[letterpaper, margin=1in, headsep=0.5in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
%\usetikzlibrary{quotes, angles}

\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{multicol}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % disable the underline of the header

\fancyhead[RE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{3cm}}
\fancyhead[L]{BECA / Dr. Huson / 10th Grade Geometry\\* Unit 8: Volume, density, area\\1 February 2020}

\begin{document}
\subsubsection*{Trajectory: Volume}
  \begin{enumerate}

    \item \#31 Jun 2108\\
    Randy’s basketball is in the shape of a sphere with a maximum circumference of 29.5 inches. Determine and state the volume of the basketball, to the nearest cubic inch.
      \begin{enumerate}
        \item What is the radius of the basketball? \vspace{2cm}
        \item What is 85\% of the volume? \vspace{2cm}
        \item (What is the volume of 2 balls?) \vspace{2cm}
      \end{enumerate}

    \item \#7 Jan 2018\\
    An ice cream waffle cone can be modeled with a right circular
    cone with a base diameter of 6.6 centimeters and a volume of $54.45 \pi$ cubic centimeters. What is the number of centimeters in the height of the waffle cone?
      \begin{enumerate}
        \item Write down the formula to use.
        \item Let $x$ be the value to be solved for. $x= \rule{4cm}{0.15mm}$
        \item Substitute the given values into the formula.
      \end{enumerate}

    Give page of text questions to be completed. (Formatting note)\\
    For each problem, complete the three modeling steps, as in the example above. Do not solve the algebra.\\
    Include scale factor examples\\
    Ask for intermediate values, like the length of a side, or the radius (strike extra words). eg:
    \item A regular pyramid has a square base. The perimeter of the base is 36 inches and the height of the pyramid is 15 inches. What is the volume of the pyramid in cubic inches?


  \end{enumerate}
\end{document}
