\documentclass[12pt, twoside]{article}
\input{../preamble}
\usepackage{float}

\title{Algebra 2}
\author{Chris Huson}
\date{December 2023}

\fancyhead[LE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{3cm} \,\\}
\fancyhead[LO]{BECA / Huson / Algebra 2: Exponentials Jan 2023 Regents \\* 4 April 2024}

\begin{document}

\subsubsection*{Regents problems: Sequences and series}
\begin{enumerate}[itemsep=0.5cm]
\item A tree farm initially has 150 trees. Each year, 20\% of the trees are cut down and 80 seedlings are planted. Which recursive formula models the number of trees, $a_n$, after $n$ years? %January 2023 Regents
\begin{enumerate}
    \item $a_1 = 150$ \\ $a_n = a_{n-1}(0.2) + 80$
    \item $a_1 = 150$ \\ $a_n = a_{n-1}(0.8) + 80$
    \item $a_n = 150(0.2)^n + 80$
    \item $a_n = 150(0.8)^n + 80$
\end{enumerate}

\item The sum of the first 20 terms of the series \(2 - 6 + 18 - 54 + \ldots\) is %January 2023 Regents
\begin{enumerate}
    \item $-610$
    \item $-59$
    \item 1,743,392,200
    \item 2,324,522,934
\end{enumerate}

% January 2019 Regents - Problem 16
\item A sequence is defined recursively by \( a_1 = 2 \) and \( a_{n+1} = 3a_n + 1 \) for \( n \geq 1 \). Find the first four terms of the sequence.

% Example Problem 2
\item Given the arithmetic sequence where \( a_1 = 5 \) and the common difference \( d = 3 \), write an explicit formula for the \( n \)th term of the sequence. What is the 10th term?

% Example Problem 3
\item A geometric sequence has a first term of \( a_1 = 4 \) and a common ratio of \( r = \frac{1}{2} \). Write the recursive formula for the sequence. Calculate the 6th term.


% January 2019 Regents - Problem 16
\item Savannah just got contact lenses. Her doctor said she can wear them 2 hours the first day, and can then increase the length of time by 30 minutes each day. If this pattern continues, which formula would not be appropriate to determine the length of time, in either minutes or hours, she could wear her contact lenses on the nth day?
\begin{enumerate}
    \item \( t_n = 120 + 30(n-1) \)
    \item \( t_n = 2 + 0.5(n-1) \)
    \item \( t_n = 2 + 30n \)
    \item \( t_n = 120 + 0.5(n-1) \)
\end{enumerate}

% January 2019 Regents - Problem 16
\item Savannah just got contact lenses. Her doctor said she can wear them 2 hours the first day, and can then increase the length of time by 30 minutes each day. If this pattern continues, which formula would not be appropriate to determine the length of time, in either minutes or hours, she could wear her contact lenses on the nth day?
\begin{enumerate}
    \item $t_n = 120 + 30(n-1)$
    \item $t_n = 2 + 0.5(n-1)$
    \item $t_n = 2 + 30n$
    \item $t_n = 120 + 0.5(n-1)$
\end{enumerate}

% January 2019 Regents - Problem 24
\item A sequence is defined recursively by $a_1 = 3$ and $a_{n+1} = 2a_n - 1$ for $n \geq 1$. What is the explicit formula for the nth term of the sequence?
\begin{enumerate}
    \item $a_n = 2^n - 1$
    \item $a_n = 2^n + 1$
    \item $a_n = 3 \cdot 2^{n-1}$
    \item $a_n = 3 \cdot 2^n - 1$
\end{enumerate}

% August 2019 Regents - Problem 12
\item The nth term of a sequence is given by $a_n = 5n - 3$. What is the 10th term of the sequence?
\begin{enumerate}
    \item 47
    \item 45
    \item 43
    \item 41
\end{enumerate}

% June 2019 Regents - Problem 8
\item Which sequence is defined recursively?
\begin{enumerate}
    \item $a_n = 3n + 1$
    \item $a_1 = 2$ and $a_{n+1} = a_n + 3$
    \item $a_n = 4n - 5$
    \item $a_n = 2^n$
\end{enumerate}

% June 2019 Regents - Problem 19
\item The first term of a sequence is $a_1 = 7$ and each subsequent term is found by adding 5 to the previous term. Which formula represents the nth term of the sequence?
\begin{enumerate}
    \item $a_n = 5n + 2$
    \item $a_n = 5n + 7$
    \item $a_n = 5n - 3$
    \item $a_n = 7n + 5$
\end{enumerate}

% June 2019 Regents - Problem 5
\item A 7-year lease for office space states that the annual rent is \$85,000 for the first year and will increase by 6\% each additional year of the lease. What will the total rent expense be for the entire 7-year lease?
\begin{enumerate}
    \item \$42,809.63
    \item \$90,425.53
    \item \$595,000.00
    \item \$713,476.20
\end{enumerate}


% June 2019 Regents - Problem 10
\item Which situation could be modeled using a geometric sequence?
\begin{enumerate}
    \item A cell phone company charges \$30.00 per month for 2 gigabytes of data and \$12.50 for each additional gigabyte of data.
    \item The temperature in your car is $79^\circ$. You lower the temperature of your air conditioning by $2^\circ$ every 3 minutes in order to find a comfortable temperature.
    \item David's parents have set a limit of 50 minutes per week that he may play online games during the school year. However, they will increase his time by 5\% per week for the next ten weeks.
    \item Sarah has \$100.00 in her piggy bank and saves an additional \$15.00 each week.
\end{enumerate}

\item Given the geometric series $300 + 360 + 432 + 518.4 \dots$, write a geometric series formula, $S_n$, for the sum of the first $n$ terms. Use the formula to find the sum of the first 10 terms, to the \emph{nearest tenth}.

\item A recursive formula for the sequence $40, 30, 22.5, \ldots$ is
\begin{enumerate}
    \item $g_n = 40 \left( \frac{3}{4} \right)^n$
    \item $g_1 = 40$ \\ $g_n = g_{n-1} -10$
    \item $g_n = 40 \left( \frac{3}{4} \right)^{n-1}$
    \item $g_1 = 40$ \\ $g_n = \frac{3}{4} g_{n-1}$
\end{enumerate}

\end{enumerate}
\end{document}