\item %2 points #29 Aug 2017
While experimenting with her calculator, Candy creates the sequence 4, 9, 19, 39, 79, $\ldots$.\\*[10 pt]
Write a recursive formula for Candy's sequence.\\*[10 pt]
Determine the eighth term in Candy's sequence.

\item %4 points #34 Aug 2017
Simon lost his library card and has an overdue library book. When the book was 5 days late, he owed \$2.25 to replace his library card and pay the fine for the overdue book. When the book was 21 days late, he owed \$6.25 to replace his library card and pay the fine for the overdue book.\\*[5 pt]
Suppose the total amount Simon owes when the book is $n$ days late can be determined by an arithmetic sequence. Determine a formula for $a_n$, the $n$th term of this sequence.\\*[5 pt]
Use the formula to determine the amount of money, in dollars, Simon needs to pay when the book is 60 days late.


\item %2 points #28 Aug 2017
Mrs. Jones had hundreds of jelly beans in a bag that contained equal numbers of six different flavors. Her student randomly selected four jelly beans and they were all black licorice.
Her student complained and said "What are the odds I got all of that kind?" Mrs. Jones replied, "simulate rolling a die 250 times and tell me if four black licorice jelly beans is unusual."\\[10pt]
Explain how this simulation could be used to solve the problem.\\

\item %2 points #28 Aug 2017
A study was designed to test the effectiveness of a new drug. Half of the volunteers received the drug. The other half received a sugar pill. The probability of a volunteer receiving the drug and getting well was 40\%. What is the probability of a volunteer getting well, given that the volunteer received the drug?
