\documentclass[12pt, twoside]{article}
\usepackage[letterpaper, margin=1in, headsep=0.5in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
%\usetikzlibrary{quotes, angles}

\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{multicol}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % disable the underline of the header

\fancyhead[LE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{4cm} \,\\}
\fancyhead[LO]{BECA / Dr. Huson / Geometry\\* Unit 6: Distance \& slope\\* 15 January 2019}

\begin{document}
\subsubsection*{7.12 Do Now: Transformations}
  \begin{enumerate}

    August 2019

    Dilation
    \item On the set of axes below, $\overline{AB}$ is dilated with a scale factor of $\frac{5}{2}$ centered at point $P$.
    
    Which of the following is/are true:
    \item $\overline{AP} \cong \overline{AA’}$
    \item $\overline{AB} \parallel \overline{A’B’}$
    \item $AB = A’B’$
    \item $\displaystyle \frac{5}{2} (A’B’) = AB$
    
    Graphing (scaffold to graph on exam stationary)
    \item The coordinates of the vertices of parallelogram $CDEH$ are $C(􏰅5,5)$, $D(2,5)$, $E(􏰅1,􏰅1)$, and $H(􏰅8,􏰅1)$. What are the coordinates of $P$, the point of intersection of diagonals $\overline{CE}$ and $\overline{DH}$?
    
    Isosceles angle situation (#6)
    Vocabulary situations: show circle with parts
    
    Given the circle, points, and line segments depicted below, circle whether each statement is true or false.
    (Circle with chords, secant, radius, diameter, arc, center, circumference, semicircle, tangent, perpendicular situations)
    
    Triangle vocabulary: vertex, side, hypotenuse, acute, obtuse, perpendicular, median, altitude, perpendicular bisector,
    {Equation of a circle competencies}

Situations with right triangle hypotenuses as circle radii. 

\item Expand the expression $(x+3)^2$ to the form $ax^2+bx+c$.
\item Factor the expression $x^+6x+9$ as a perfect square.
\item Simplify the radical $\sqrt{50}$.

What are the coordinates of the center and the length of the radius of the circle whose equation is $x^2 + y^2 = 8x -6y +39$?

Angle measures
\item Use the tangent function to determine the measure of the central angle $\theta$.
\item A regular pentagon is inscribed in a circle as shown below. What is the measure of the central angle between two consecutive vertices, $m\angle AOB$?

Formulas for the area and circumference of circles:
$A=\pi r^2$
$C=\pi D = 2\pi r$

\item Find the area of a circle with radius 4 cm.
\item Find the radius of a circle having an area of $25 \pi$.


\newpage
  \item The line $-3x+4y=8$ is transformed by a dilation centered at the origin. Which linear equation could represent its image?
  \begin{multicols}{2}
  \begin{enumerate}
    \item $\displaystyle y=\frac{4}{3}x+8$
    \item $\displaystyle y=\frac{3}{4}x+8$
    \item $\displaystyle y=-\frac{3}{4}x-8$
    \item $\displaystyle y=-\frac{4}{3}x-8$
    \end{enumerate}
  \end{multicols}

  \item Apply a dilation mapping $\triangle ABC \rightarrow \triangle A'B'C'$ with a factor of $k=2$ centered at $(3,3)$. Draw and label the image on the grid and make a table of the coordinates.
    \begin{flushright} %4 quadrant regents grid w T-Chart
    \begin{tikzpicture}[scale=.635]
      \draw [help lines] (-3,-3) grid (10,8);
      \draw [thick, ->] (-3.2,0) -- (10.4,0) node [below right] {$x$};
      \draw [thick, ->] (0,-3.2)--(0,8.4) node [left] {$y$};
      \draw [thick] (1,3)--(4,1)--(5,5)--cycle;
      \draw [fill] (1,3) circle [radius=0.1]node[below left]{$A$};
      \draw [fill] (4,1) circle [radius=0.1]node[below left]{$C$};
      \draw [fill] (5,5) circle [radius=0.1]node[above left]{$B$};
      \draw [fill] (3,3) circle [radius=0.1];
    \end{tikzpicture}
    \end{flushright}
    
  \item Find the image of $P(3,5)$ after a reflection over the $x$-axis.  \vspace{2cm}

  \item What transformation maps $\triangle ABC$ onto $\triangle DEF$, shown below? Fully specify the transformation.
    \begin{flushright}
      \begin{tikzpicture}[scale=.48]
      \draw [help lines] (-7,-5) grid (10,10);
      \draw [thick, <->] (-7.4,0) -- (10.4,0) node [right] {$x$};
      \draw [thick, <->] (0,-5.4)--(0,10.4) node [above] {$y$};  
      \draw [thick]
      (-5,-2) node[below left] {$A$}--
      (-3,3) node[right] {$B$}--
      (-2,-1) node[right] {$C$}--cycle;  
      \draw [thick]
      (7,3) node[below right] {$D$}--
      (5,8) node[right] {$E$}--
      (4,4) node[left] {$F$}--cycle; 
    \end{tikzpicture}
  \end{flushright}

\newpage
  \item Plot two transformations. Rotate $\triangle ABC$ clockwise $90^\circ$ around the origin, then reflect the result across the $x$-axis. Make a table of the coordinates and plot and label the images on the axes. %$\triangle ABC \rightarrow \triangle A'B'C'$ 
  \begin{flushright}
    \begin{tikzpicture}[scale=.48]
      \draw [help lines] (-9,-8) grid (9,9);
      \draw [thick, <->] (-9.4,0) -- (9.4,0) node [right] {$x$};
      \draw [thick, <->] (0,-8.4)--(0,9.4) node [above] {$y$};  
      \draw [thick]
        (-4,2) node[below left] {$A$}--
        (-1,7) node[above] {$B$}--
        (-1,2) node[below] {$C$}--cycle;  
  \end{tikzpicture}
  \end{flushright}

  \item A translation maps $A(-2, 1) \rightarrow A'(5,1)$. What is the image of $B(3,-1)$ under the same translation? \vspace{1cm}

  \item Reflect $\triangle ABC$ over the $y$-axis. Plot and label the image on the axes and make a table of the coordinates showing $\triangle ABC \rightarrow \triangle A'B'C'$.
  \begin{flushright}
      \begin{tikzpicture}[scale=.48]
      \draw [help lines] (-8,-7) grid (8,7);
      \draw [thick, <->] (-8.4,0) -- (8.4,0) node [right] {$x$};
      \draw [thick, <->] (0,-7.4)--(0,7.4) node [above] {$y$};  
      \draw [thick]
        (-2,-3) node[below left] {$A$}--
        (3,4) node[above left] {$B$}--
        (5,-1) node[below right] {$C$}--cycle;  
    \end{tikzpicture}
  \end{flushright}

\end{enumerate}
\end{document}