\documentclass{beamer}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{venndiagram}

%\usepackage{pgfplots}
%\pgfplotsset{width=10cm,compat=1.9}
%\usepackage{pgfplotstable}

\setlength{\headheight}{26pt}%doesn't seem to fix warning

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}

\lhead{\small{BECA / Dr. Huson / 11.1 IB Math Unit 4}}



\title{Mathematics Class Slides}
\subtitle{Bronx Early College Academy}
\author{Chris Huson}
\date{19 November - 30 November 2018}

\begin{document}

\frame{\titlepage}

\section[Outline]{}
\frame{\tableofcontents}

  \section{4.1 Drui: Exponent rules, Monday Nov 19}
    \frame
    {
      \frametitle{GQ: How do we manipulate exponential expressions?}
      \framesubtitle{CCSS: HSF.IF.C.7 Analyze functions  \hspace{\stretch{1}}  \alert{4.1  Monday Nov 19}}

      \begin{block}{Do Now: Skills check p. 100}
      \end{block}
      Review Exam\\
      Exponent operations p. 100-104 \\ \bigskip
      Homework: Exercises 4A p. 104
    }

  \section{4.2 Drui: Laptop, Deltamath, Desmos /Word. Tuesday Nov 20}
    \frame
    {
      \frametitle{How do we communicate mathematical results?}
      \framesubtitle{CCSS: MP.4 Model with mathematics \hspace{\stretch{1}} \alert{4.2 Tuesday Nov 13}}

      \begin{block}{Technical skills needed to communicate mathematics}
      \begin{enumerate}
          \item Word processing: Microsoft Word and equation editor
          \item Computer calculators: Desmos; domain restriction, labeling
          \item Cloud storage: Dropbox
          \item Technical writing standards: MLA format (Purdue OWL)
          \item Writing style: declarative
          \item Assessment criteria: IB exploration criterion \emph{B: Mathematics Presentation}
      \end{enumerate}
      \end{block}
      Deltamath exponential practice. Homework: complete Deltamath \\
      Makeup: Rewrite Quadratics paper, using model as guide}

  \section{4.3 Drui: Exponential functions, Wednesday Nov 21}
    \frame
    {
      \frametitle{GQ: How do we understand exponential functions?}
      \framesubtitle{CCSS: HSF.IF.C.7 Analyze functions  \hspace{\stretch{1}}  \alert{4.3  Wednesday Nov 21}}

      \begin{block}{Do Now: Exercise \#4C p. 107}
      \end{block}
      %Review formula sheets\\
      Solving exponent equations \#4D p. 108 \\
      Exponential functions, p. 109-114\\ \bigskip
      Homework: Exercises 4F p. 114 (review 4B-4E)
    }

  \section{4.4 Drui: Intro to logarithms, Monday Nov 26}
    \frame
    {
      \frametitle{GQ: How do we define logarithms?}
      \framesubtitle{CCSS: HSF.IF.C.7 Analyze functions  \hspace{\stretch{1}}  \alert{4.4 Monday Nov 26}}

      \begin{block}{Do Now: Exponent exercises handout}
      \end{block}
      %Review formula sheets\\
      Review exponential function transformation homework \#4G p. 114 \\
      Compound interest exploration p. 111\\
      Properties of logarithms, p. 115-6\\\bigskip
      Homework: Exercises 4G, 4H p. 115-6\\
      \alert{Parent-teacher conferences Thursday \& Friday}
    }

    \section{4.5 Drui: Laptop, Deltamath, Desmos Tuesday Nov 27}
      \frame
      {
        \frametitle{How do we work with logarithms?}
        \framesubtitle{CCSS: MP.4 Model with mathematics \hspace{\stretch{1}} \alert{4.5 Tuesday Nov 27}}

        \begin{block}{Technical skills needed to communicate mathematics}
        \begin{enumerate}
            \item Word processing: Microsoft Word and equation editor
            \item Computer calculators: Desmos; domain restriction, labeling
            \item Cloud storage: Dropbox
            \item Technical writing standards: MLA format (Purdue OWL)
            \item Writing style: declarative
            \item Assessment criteria: IB exploration criterion \emph{B: Mathematics Presentation}
        \end{enumerate}
        \end{block}
        Deltamath exponents \& logarithm practice.\\
        Homework: complete Deltamath\\
        \alert{Parent-teacher conferences Thursday \& Friday}
        }

  \section{4.6 Drui: Logarithmic functions, Wednesday Nov 28}
    \frame
    {
      \frametitle{GQ: How do we understand logarithmic functions?}
      \framesubtitle{CCSS: HSF.IF.C.7 Analyze functions  \hspace{\stretch{1}}  \alert{4.6 Wednesday Nov 28}}

      \begin{block}{Do Now: Exponent exercises handout}
      \end{block}
      Review exponential function transformation homework 4G, 4H p. 115-6\\
      Logarithmic functions, p. 118-9\\ \bigskip
      Homework: Exercises 4J p. 119\\
      \alert{Parent-teacher conferences tomorrow \& Friday}
    }

  \section{4.7 Drui: Logarithm bases, Thursday Nov 29}
    \frame
    {
      \frametitle{GQ: How do we use different logarithm bases?}
      \framesubtitle{CCSS: HSF.IF.C.7 Analyze functions  \hspace{\stretch{1}}  \alert{4.7 Thursday Nov 29}}

      \begin{block}{Do Now: Logarithm exercises handout}
      \end{block}
      %Review formula sheets\\
      Logarithmic functions, p. 119-122\\ \bigskip
      Homework: Exercises 4K, 4L p. 120-122; weekend packet\\
      \alert{Parent-teacher conferences today \& tomorrow}
    }

  \section{4.8 Drui: Laws of logarithms, Monday Dec 3}
    \frame
    {
      \frametitle{GQ: How do we manipulate logarithmic expressions?}
      \framesubtitle{CCSS: HSF.IF.C.7 Analyze functions  \hspace{\stretch{1}}  \alert{4.8 Monday Dec 3}}

      \begin{block}{Do Now: Logarithm exercises handout}
      \end{block}
      Logarithmic expressions \& equations, p. 122-124\\ \bigskip
      Homework: Exercises 4M p. 124
    }

  \section{4.9 Drui: Laptop, Deltamath, Desmos Tuesday Dec 4}
    \frame
    {
      \frametitle{How do we work with logarithms?}
      \framesubtitle{CCSS: MP.4 Model with mathematics \hspace{\stretch{1}} \alert{4.9 Tuesday Dec 4}}

      Deltamath exponents \& logarithm practice.\\
      Homework: complete Deltamath\\
      }

  \section{4.10 Drui: Logarithms change of base, Wednesday Dec 5}
    \frame
    {
      \frametitle{GQ: How do we change of base of logarithmic expressions?}
      \framesubtitle{CCSS: HSF.IF.C.7 Analyze functions  \hspace{\stretch{1}}  \alert{4.10 Wednesday Dec 5}}

      \begin{block}{Do Now: Logarithm exercises, simplify}
        \begin{enumerate}
            \item $\log_3 6 + \log_3 15$
            \item $\log_4 8 - \log_4 2$
            \item $\log a + \log b - \log c$
            \item $\displaystyle \log_7 14 + \log_7 \frac{1}{2}$
            \item $\ln e^3 +\ln e^{-1}$
        \end{enumerate}
      \end{block}
      Logarithmic expressions, 4.7 Solving equations, p. 125-8\\ \bigskip
      Homework: Exercises 4O p. 126
    }

  \section{4.11 Drui: Exponential \& logarithm function applications, Thursday Dec }
    \frame
    {
      \frametitle{GQ: How do we model exponential situations?}
      \framesubtitle{CCSS: HSF.IF.C.7 Analyze functions  \hspace{\stretch{1}}  \alert{4.11 Thursday Dec 6}}

      \begin{block}{Do Now: Change each expression to one in terms of $\log_{10}$}
        \begin{enumerate}
            \item $\log_3 6$
            \item $\log_2 20$
            \item $\log_a b$
            \item $\ln 121$
        \end{enumerate}
      \end{block}
      4.8 Applications, p. 128-133\\ \bigskip
      Homework: Exercises 4P \& 4Q p. 128-9 (handout)
    }

\end{document}
