\documentclass{beamer}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{quotes, angles}
\usepackage{graphicx}

%\usepackage{pgfplots}
%\pgfplotsset{width=10cm,compat=1.9}
%\usepackage{pgfplotstable}

\setlength{\headheight}{26pt}%doesn't seem to fix warning

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

%\rhead{\small{13 November 2018}}
\lhead{\small{BECA / Dr. Huson / Geometry Unit 3}}

\renewcommand{\headrulewidth}{0pt}

\title{Mathematics Class Slides}
\subtitle{Bronx Early College Academy}
\author{Chris Huson}
\date{26 November 2018}

\begin{document}
\frame{\titlepage}
\section[Outline]{}
\frame{\tableofcontents}


\section{4.1 Project: Triangle congruence project, Monday 26 November}
  \frame
  {
    \frametitle{Construction project: Triangle congruence}
    \framesubtitle{CCSS: HSG.CO.C.9 Prove geometric theorems \hspace{\stretch{1}} \alert{4.1}}

    \begin{block}{Four pages of $\triangle$ duplication for your binder}
    \begin{enumerate}
        \item Side-side-side (SSS)
        \item Side-angle-side (SAS)
        \item Angle-side-angle (ASA)
        \item Side-side-angle (SSA), false, ``ambiguous case"
    \end{enumerate}
        Grading criteria (20 points)
    \begin{enumerate}
        \item Complete and correct construction
        \item State postulate or theorem. (written steps not necessary)
        \item MLA header, center title \& last name on right
        \item Precise, elegant, mathematical aesthetic
    \end{enumerate}
    \end{block}
    Due Friday November 30
    }

  \section{4.1 Drui: Triangle congruence. Monday 26 November}
    \frame
    {
      \frametitle{GQ: How do we construct congruent triangles?}
      \framesubtitle{CCSS: HSG.CO.C.9 Prove geometric theorems \hspace{\stretch{1}} \alert{4.1 Monday 26 November}}

      \begin{block}{Do Now: }
        \begin{enumerate}
          \item Trig review problems handout
          \item $+, \triangle$ What is working? What would you change?
        \end{enumerate}
      \end{block}
      Seating chart \\
      2nd trimester norms and expectations \\
      $\triangle$ congruence construction project, SSS\\
      Homework packet review, trig problems \\[0.5cm]
      Homework: Distance, midpoint, and slope review, handout
    }


  \section{4.2 Drui: Deltamath. Tuesday 27 November}
    \frame
    {
      \frametitle{GQ: How do we use trigonometric ratios?}
      \framesubtitle{CCSS: HSG.CO.D.12 Congruence, geometric constructions \hspace{\stretch{1}} \alert{4.2 Tuesday 27 November}}

      \begin{block}{Do Now: SAS $\triangle$ congruence}
      \begin{enumerate}
          \item Duplicate a side, duplicate an angle, duplicate a side.
          \item Angle must be the \emph{included} angle, between the two sides
          \item $\triangle ABC \cong \triangle A'B'C'$ iff $\overline{AB} \cong \overline{A'B'}, \angle A \cong \angle A', \text{ and } \overline{AC} \cong \overline{A'C'}$
      \end{enumerate}
      \end{block}
      Geogegra intro (?)\\
      Deltamath assessment: distance, midpoint, and slope\\[0.5cm]
      Homework: Complete deltamath (10pm deadline)
    }


  \section{4.3 Drui: Triangle proofs. Wednesday 28 November}
    \frame
    {
      \frametitle{GQ: How do we prove triangles congruent?}
      \framesubtitle{CCSS: HSG.CO.D.12 Congruence, geometric constructions \hspace{\stretch{1}} \alert{4.3 Wednesday 28 November}}
      Do Now: Theorems review handout \\
      Triangle sum, transversal, vertical
      \begin{block}{Angle-side-angle (ASA) $\triangle$ congruence}
      \begin{enumerate}
          \item Duplicate an angle, duplicate a side, duplicate an angle
          \item $\triangle ABC \cong \triangle A'B'C'$ iff $\angle A \cong \angle A', \overline{AB} \cong \overline{A'B'}, \text{ and } \angle B \cong \angle B'$
      \end{enumerate}
      \end{block}
      Lesson: \\
      Triangle congruence proofs\\
      Assessment: distance, midpoint, and slope\\[0.5cm]
      Homework: Pretest packet. \alert{Test Friday}
    }

  \section{4.4 Drui: Pretest review. Thursday 29 November}
    \frame
    {
      \frametitle{GQ: How do we prove triangles congruent?}
      \framesubtitle{CCSS: HSG.CO.D.12 Congruence, geometric constructions \hspace{\stretch{1}} \alert{4.4 Thursday 29 November}}

      Do Now: Triangle congruence practice handout

      \begin{block}{SSA $\triangle$ congruence (or ASS, ``jack ass theorem")}
      \begin{enumerate}
          \item Duplicate an angle, duplicate a side, duplicate an side
          \item Given $\triangle ABC$ if $ \angle A \cong \angle A', \overline{AB} \cong \overline{A'B'}, \text{ and } \overline{BC} \cong \overline{B'C'}$ then two possible $\triangle$s may result.
      \end{enumerate}
      \end{block}
      Lesson: \\
      Review pretest packet\\[0.5cm]
      Homework: Study for \alert{test tomorrow}
    }

  \section{4.5 Drui: Exam. Friday 30 November}
    \frame
    {
      \frametitle{GQ: How do we prove triangles congruent?}
      \framesubtitle{CCSS: HSG.CO.D.12 Congruence, geometric constructions \hspace{\stretch{1}} \alert{4.5 Friday 30 November}}

      \begin{block}{Unit exam}
      \end{block}
      Triangle congruence project due\\[0.5cm]
      Homework: Review packet
    }

\end{document}
