\documentclass[12pt, oneside]{article}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Name: \hspace{1.5in} }
\lhead{BECA / Dr. Huson / IB Math SL \\* 17 January 2018 \\* Classwork: Regents exponents problems}

\vspace{1cm}

\renewcommand{\headrulewidth}{0pt}

\title{Worksheet and test template}
\author{Chris Huson}
\date{January 2018}

\begin{document}

\begin{enumerate}
\subsection*{Rational exponents and radicals}

\item Write $\sqrt[6]{x} \cdot \sqrt{x}$ as a single term with a rational exponent.

\item True of false:  $\displaystyle \big( 27^\frac{2}{9} \big) $ can be written as the equivalent radical expression $\sqrt[3]9$

\item For $x \neq 0$, which expressions are equivalent to one divided by the sixth root of $x$?
\[ \text{I. } \frac{\sqrt[6]{x}}{\sqrt[3]{x}} \text{  II. } \frac{x^{\frac{1}{6}}}{x^{\frac{1}{3}}} \text{  III. } x^{-\frac{1}{6}} \]

\subsection*{Polynomial algebra procedures}
\item Simplify $(x-3)(-2x^2+5x+1)$
\item Is 3 a zero of the function $f(x)=x^3-2x-20$?

\item Given $r(x)=x^3-4x^2+4x-6$, find the value of $r(2)$.\\*
What does your answer tell you about $x-2$ as a factor of $r(x)$? Explain.

\item A manufacturing company has developed a cost model,\\* $C(x)=0.15x^3 +0.01x^2+2x+120$, where $x$ is the number of items sold, in thousands. The sales price can be modeled by $S(x)=30-0.01x$. Therefore, revenue is modeled by $R(x)=x \cdot S(x)$.\\*[12pt]
The company’s profit, $P(x)=R(x)-C(x)$, could be modeled by what polynomial?

\subsection*{Graphing calculator solutions}
\item Given $f(x) = 3|x|-1$ and $g(x)=0.03x^3-x+1$. Graph the two functions and make a quick sketch. Find the two solutions for the equation $f(x)=g(x)$, stating them as ordered pairs rounded to the nearest hundredth.

\subsection*{Function transformations}
\item Given the parent function $p(x) = \cos x$, which phrase best describes the transformation used to obtain the graph of $g(x)=cos(x+a)-b$, if $a$ and $b$ are positive constants?\\*
(1) right $a$ units, up $b$ units\\*
(2) right $a$ units, down $b$ units\\*
(3) left $a$ units, up $b$ units\\*
(4) left $a$ units, down $b$ units

\subsection*{Exponential models, base change}
\item A student studying public policy created a model for the population of Detroit, where the population decreased 25\% over a decade. He used the model $P=714(0.75)^d$, where $P$ is the population, in thousands, $d$ decades after 2010. Another student, Suzanne, wants to use a model that would predict the population after $y$ years. Suzanne’s model is best represented by\\*
(1) $P=714(0.6500)^y$ (3) $P=714(0.9716)^y$\\* 
(2) $P=714(0.8500)^y$ (4) $P=714(0.9750)^y$

\item A radioactive substance has a mass of 140 g at 3 p.m. and 100 g at 8 p.m. Write an equation in the form $\displaystyle A=A_0\left(\frac{1}{2}\right)^{\frac{t}{h}}$ that models this situation, where $h$ is the constant representing the number of hours in the half-life, $A_0$ is the initial mass, and $A$ is the mass $t$ hours after 3 p.m.\\*[12pt]
Using this equation, solve for $h$, to the \textit{nearest ten thousandth}.\\*[12pt]
Determine when the mass of the radioactive substance will be 40 g. Round your answer to the nearest tenth of an hour.
   

\subsection*{Logarithms}
\item What is the $\log_3{27}$?
\item Simplify $\ln{18}-\ln{2}$
\item What is the exact solution to $8(2^{x + 3}) = 48$?

\subsection*{Imaginary numbers}
\item Simplify $9i+(2i)^3$
\item Use the quadratic formula to find the solution to the equation $4x^2+98=0$.
\item The expression $6xi^3(-4xi + 5)$ is equivalent to...

\newpage

\item Algebraically determine the values of $h$ and $k$ to correctly complete the identity stated below. \[2x^3-10x^2 +11x - 7 = (x - 4)(2x^2 + hx + 3) + k\]\\*[105pt]

\item Given the exponential function $\displaystyle f(x)=17e^{(0.15x)}$.
\begin{enumerate}
    \item Write down $f(0)$.\\*[25pt]
    \item Find $f(2)$.\\*[25pt]
    \item Solve for $x$ such that $f(x)=25$.\\*[95pt]
\end{enumerate}

\item Express $(1-i)^3 \text{ in } a+bi$ form. 

\end{enumerate}
\end{document}