\documentclass[12pt, twoside]{article}
\input{../preamble}

\title{IB Mathematics}
\author{Chris Huson}
\date{April 2024} %previously March 2022, 5.6 Exit Note: Compound Interest

\fancyhead[LE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{1cm} \,\\}
\fancyhead[LO]{BECA/Huson/Algebra II 4: Exponential functions \& Rational Exponents \\* 3 April 2024}

\begin{document}

\subsubsection*{4.7 PreExam: Exponential Functions and Compound Interest}
Construct an exponential function symbolically given a description of the relationship \hfill F.LE.2.ii \\[0.5cm]
\emph{Compound interest formula:} \\
$\displaystyle FV=PV \times \left(1+\frac{r}{100k} \right)^{kn}$
where FV is the future value,\\[0.25cm]
PV is the present value, n is the number of years, \\
 k is the number of compounding periods per year, \\
 r\% is the nominal annual rate of interest

\begin{enumerate}
\item Write down the formula for a function $f(x)$ that increases 15\% for each increase of 1 in input value $x$. \vspace{2cm}
\item The price of a share of stock in a particular company is \$2.25 per share in 2010. Assume that it increases in value by 6\% annually thereafter. 
\begin{enumerate}
    \item 	Write an equation representing the value of the stock $P(t)$, in dollars, $t$ years after 2010. \vspace{2cm}
    \item What does $P(30)$ represent in this context? \vspace{2cm}
\end{enumerate}

\item An investment of \$5,000 compounds monthly with an annual interest rate of 4\%.
\begin{enumerate}[itemsep=0.5cm]
    \item How many compounding periods are there per year? \\[0.25cm]
    $k=$
    \item First write the formula for, and then calculate, the account balance of principal and interest after three years.
\end{enumerate} \vspace{2cm}

\newpage
\item The graph shows the exponential function $\displaystyle f(x)$.
\begin{multicols}{2}
    \begin{enumerate}[itemsep=1cm]
        \item Write down the initial value of the function.
        \item By what factor do the values of $f$ increase each time $x$ increases by 1?
        \item By what factor would $f$ increase when the input increases by 10?
    \end{enumerate}
    \begin{center}
    \begin{tikzpicture}[x=1cm, y=0.15cm, xscale=2]
        \draw [thin, color=lightgray, xstep=0.5cm,ystep=0.75cm] (0,0) grid (3,40);
        \draw [thick, ->] (0,0) -- (+3.3,0) node [below]{$x$};
        \draw [thick, ->] (0,0) -- (0,43) node [right]{$y$};        
        \foreach \x in {0,0.5,...,3}
            \draw (\x cm,0) -- (\x cm,0) node[below] {$\x$};
        \foreach \y in {0,10,20,...,40}
            \draw[shift={(0,\y)}] (2pt,0pt)--(-2pt,0pt) node[left]{$\y$};
        \draw [thick, ->, smooth,domain=0.:3.2] plot(\x,{10*(1.5^\x)}) node[below right]{$f$};
        \fill (0,10) ellipse [x radius=1pt, y radius=2pt]  node [below right] {$(0,10)$};
        \fill (1,15) ellipse [x radius=1pt, y radius=2pt] node [below right] {$(1,15)$};
    \end{tikzpicture}
    \end{center}
    \end{multicols}

\item A company depreciates a piece of equipment which was purchased in 2022 at a constant annual rate. The equation representing the value of the equipment $V(t)$, in dollars, $t$ years after 2022 is $\displaystyle V(t)=12,000 \times (0.85)^t$.

\begin{multicols}{2}
    \begin{enumerate}[itemsep=1cm]
        \item Write down the initial value of the equipment.
        \item What does the value 0.85 tell us about the situation? \vspace{1cm}
        \item By what percent does the equipment's value decrease each year?
        \item Sketch the graph of the function.
    \end{enumerate}
    \begin{center}
    \begin{tikzpicture}[x=1cm, y=0.005cm, xscale=1]
        \draw [thin, color=lightgray, xstep=1cm,ystep=1cm] (0,0) grid (5,1605);
        \draw [thick, ->] (0,0) -- (+5.3,0) node [below]{$t$};
        \draw [thick, ->] (0,0) -- (0,1700) node [right]{$y$};        
        \foreach \x in {0,1,...,5}
            \draw (\x cm,0) -- (\x cm,0) node[below] {$\x$};
        \foreach \y in {0,200,...,1600}
            \draw[shift={(0,\y)}] (2pt,0pt)--(-2pt,0pt) node[left]{$\y$};
        %\draw [thick, ->, smooth,domain=0.:5.2] plot(\x,{1200*(0.85^\x)});
    \end{tikzpicture}
    \end{center}
    \end{multicols}

\end{enumerate}
\end{document}