\documentclass[12pt, twoside]{article}
\input{../preamble}
\usepackage{float}

\title{Algebra 2}
\author{Chris Huson}
\date{May 2024}

\fancyhead[LE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{1.5cm} \,\\}
\fancyhead[LO]{BECA/Huson/Algebra 2: Regents Preparation \\* 28 May 2024}

\begin{document}

\subsubsection*{Prep \#18: Quadratics \hfill Refer to your formula sheet}
\begin{enumerate}[itemsep=0.5cm]
\item Round to the accuracy stated.
    \begin{multicols}{2}
    \begin{enumerate}[itemsep=1cm]
        \item nearest whole: $125.02$
        \item nearest tenth: $33.550$
        \item nearest hundredth: $0.8149$
        \item nearest thousandth: $2.718281828 \dots$
    \end{enumerate}
    \end{multicols} \vspace{0.5cm}

\item Write each expression in standard form.
    \begin{multicols}{2}
    \begin{enumerate}[itemsep=0.5cm]
        \item $5x-3x^2+8x^2+7$
        \item $2(3x+y)(x-4y)$
    \end{enumerate}
    \end{multicols} \vspace{4cm}

\item Simplify. (assume $x > 0$) \hfill N.RN.2 Properties of exponents
    \begin{multicols}{2}
    \begin{enumerate}[itemsep=1cm]
        \item $x^2 \cdot x^3 =$
        \item $\displaystyle \frac{x^{\frac{2}{3}}}{x^{\frac{1}{6}}} =$
        \item $\sqrt[3]{x^6} =$
        \item $\displaystyle \frac{\sqrt{36x^6}}{\sqrt[3]{27x^6}} = $
    \end{enumerate}
    \end{multicols} \vspace{1cm}


\item Simplify each complex expression to the form $a+bi$. \hfill N.CN.2 Complex numbers
    \begin{multicols}{2}
    \begin{enumerate}
        \item $(11-2i) - (6-7i)=$
        \item $(6+3i)(1-4i)=$
    \end{enumerate}
    \end{multicols} \vspace{3cm}

\newpage
\item Solve for $x$ over the complex numbers. \\[0.25cm]
$x^2-4x+13=0$
\vspace{5cm}

\item Solve algebraically for all values of $x$. \\[0.25cm]
$\sqrt{x+12}=x$ \vspace{5cm}

\item Solve algebraically for all values of $x$. \\[0.25cm]
$\displaystyle \frac{1}{x+12}=x$

\newpage
\item Write a recursive formula for the sequence 16, 8, 0, $-8$, $\ldots$ \vspace{2cm}

\item A sequence is defined by the recursive formula
\begin{align*}
a_1 &= 30 \\
a_{n} &= a_{n-1}+5
\end{align*}
Write an explicit formula for the sequence. \vspace{2cm}


\item The sum of the first $n$ terms of the geometric sequence beginning $1$, $1.5$, $2.25$, $\ldots$ is 171, rounded to \emph{the nearest integer}. Find $n$. \vspace{2cm}

%F.LE.2: Construct a linear or exponential function symbolically given: a graph, a description of the relationship, or two input-output pairs (including from a table).
\item Complete the table for the geometric sequence $a$.
    \begin{center}
    \begin{tabular}{|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
        \hline
        $n$ & 1 & 2 & 3 & 4 & 5 \\
        \hline
        $a_n$ & 100 & 80 & & & \\[0.25cm]
        \hline
    \end{tabular}
    \end{center}
    Model the sequence with an exponential function.


\newpage
\item A survey was conducted to compare the dietary habits of American and Japanese families. Families were asked which they had eaten for dinner most recently, meat or fish. The proportions of each answer are shown in the table below.
    \begin{center}
        \begin{tabular}{|c|c|c|c|}
            \hline
            Nationality & Meat & Fish & Total \\[0.2cm]
            \hline
            Americans & 0.78 & 0.22 & 1.00 \\[0.25cm]
            \hline
            Japanese & 0.43 & 0.57 & 1.00 \\[0.25cm]
            \hline
        \end{tabular}
    \end{center}
    \begin{enumerate}
        \item Does the survey data indicate that Americans and Japanese families have similiar dietary habits? Justify your answer. \vspace{2cm}
        \item 200 American families and 100 Japanese families participated in the survey. Calculate the number of each category of response and enter it in the appropriate cell in the table below. 
        \begin{center}
            \begin{tabular}{|c|p{1.5cm}|p{1.5cm}|c|}
                \hline
                Nationality & \; Meat & \; Fish & Total \\[0.2cm]
                \hline
                Americans & &  & 200 \\[0.25cm]
                \hline
                Japanese & &  & 100 \\[0.25cm]
                \hline
            \end{tabular}
        \end{center}
        \item The survey was conducted in Kansas City (an inland city) and Tokyo (a city on the Pacific Ocean). How might that affect the survey's findings? 
    \end{enumerate} \vspace{3cm}

\newpage
\item A manufacture of portable speakers finds that its profit varies depending on the number of speakers it makes. The profit, $p(x)$, in thousands of dollars as a function of the number of speakers, $x$, in thousands is modeled by $$p(x) = -x^3+7x^2+6x-25$$
\begin{enumerate}
    \item Graph $y=p(x)$, over the interval $0 \leq x \leq 8$ on the set of axes below.
    \item Over the given interval, state the coordinates of the maximum of $p$ rounding all values to the \emph{nearest integer}. Explain what the point means in terms of the number of speakers and profit. \vspace{3cm}
\end{enumerate}
\begin{center}
    \begin{tikzpicture}[yscale=0.1]
        \draw[gray,thin, xstep=1cm,ystep=10cm] (-3,-41) grid (10,80);
        \draw [thick,<->] (-3.5,0)--(10.5,0) node [right] {$x$};
        \draw [thick,<->] (0,-45)--(0,85) node [above] {$y$};
        \foreach \x in {1}
            \draw[thick] (\x cm,50pt) -- (\x cm,-50pt) node[below] {$\x$};
        \foreach \y in {20}
            \draw[thick] (4pt,\y cm)--(-4pt,\y cm) node[left]{$\y$};
        %\draw [thick,<->] plot[smooth, domain=-2.2:8] (\x, {-(\x*\x*\x)+7*(\x*\x)+6*(\x)-25});
    \end{tikzpicture}
    \end{center}

\newpage
\item Over the set of integers, factor the function $f(x) = x^4-5x^2+4$. \vspace{10cm}

\item Given the function $P(x) = x^3-3x^2-2x+4$, find the value of $P(-1)$ and $P(1)$.\\[5cm]
Now identify the correct statement.
\begin{enumerate}
    \item $(x-1)$ is a factor because $P(-1)=2$.
    \item $(x+1)$ is a factor because $P(-1)=2$.
    \item $(x+1)$ is a factor because $P(1)=0$.
    \item $(x-1)$ is a factor because $P(1)=0$.
\end{enumerate}

\newpage

\item The data in the table was graphed and then a smooth curve was fit through the points. Write down an equation for the exponential function $f(x)$ shown.
    \begin{flushright}
    \begin{tabular}{|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
        \hline
        $n$ & 1 & 2 & 3 & 4 & 5 \\
        \hline
        $a_n$ & 100 & 80 & & & \\[0.25cm]
        \hline
    \end{tabular}
    \end{flushright}
    \begin{flushright}
    \begin{tikzpicture}[x=1cm, y=0.1cm, xscale=1.5]
        \draw [thin, color=lightgray, xstep=1cm,ystep=0.5cm] (0,0) grid (4,51);
        \draw [thick, ->] (0,0) -- (+4.3,0) node [below]{$x$};
        \draw [thick, ->] (0,0) -- (0,53) node [right]{$y$};        
        \foreach \x in {1}
            \draw (\x cm,5pt) -- (\x cm,-5pt) node[below] {$\x$};
        \foreach \y in {0,10,...,50}
            \draw[shift={(0,\y)}] (2pt,0pt)--(-2pt,0pt) node[left]{$\y$};
        \draw [thick, ->, smooth,domain=0.:4.2] plot(\x,{15*(3^(\x/4))});
        \fill (0,15) ellipse [x radius=1.33pt, y radius=2pt];
        \fill (4,45) ellipse [x radius=1.33pt, y radius=2pt];
    \end{tikzpicture}
    \end{flushright}

\item An investment of \$4000 earns a continuous interest rate of 8\%. On the axes below, graph the value of the investment $v(t)$ in thousands of dollars versus time $t$ in years. 
\begin{center}
    \begin{tikzpicture}[scale=0.8]
        \draw[gray,thin] (0,0) grid (10,10);
        \draw [thick,->] (0,0)--(10.5,0) node [right] {$t$};
        \draw [thick,->] (0,0)--(0,10.5) node [above] {$v(t)$};
        \foreach \x in {0,1,...,10}
            \draw (\x cm,5pt) -- (\x cm,-5pt) node[below] {$\x$};
        \foreach \y in {0,1,...,10}
            \draw[shift={(0,\y)}] (2pt,0pt)--(-2pt,0pt) node[left]{$\y$};
    \end{tikzpicture}
    \end{center}
Find the value of the investment after 5 years rounding to the \emph{nearest dollar}.

\newpage
\item Biologists are studying a new bacterium. They create a culture with 100 of the bacteria and
anticipate that the number of bacteria will double every 30 hours. Write an equation for the
number of bacteria, $B$, in terms of the number of hours, $t$, since the experiment began. %Jan 2020
\vspace{3cm}

\item During the summer, Adam saved \$4000 and Betty saved \$3500. Adam deposited his money in
Bank A at an annual rate of 2.4\% compounded monthly. Betty deposited her money in Bank B at
an annual rate of 4\% compounded quarterly. Write two functions that represent the value of each
account after $t$ years if no other deposits or withdrawals are made, where Adam's account value is represented by $A(t)$, and Betty's by $B(t)$. \vspace{5cm}
%Jan 2024

\item Solve algebraically for $x$ that makes the function value 125, to the \emph{nearest hundredth}, $f(x)=100 \times 10^{x}$. 

\end{enumerate}
\end{document}