\documentclass[12pt, twoside]{article}
\input{../preamble}
\usepackage{siunitx}

\title{IB Mathematics}
\author{Chris Huson}
\date{May 2024}

%\fancyhead[LE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{1cm} \,\\}
\fancyhead[LO]{BECA/Huson/Algebra II: Regents Prep \\* 6 May 2024}

\begin{document}

\subsubsection*{Practice Regents problems \#6}
AII-F.BF.2: Write arithmetic and geometric sequences both recursively and with an explicit formula, use them to model situations, and translate between the two forms.

\begin{enumerate}
\item Given the sequence $a$: 2, 5, 8, 11, $\ldots$
\begin{enumerate}[itemsep=4cm]
    \item State whether the sequence is arithmetic, geometric, or neither. Justify your answer.
    \item Write a recursive formula for $a$.
    \item Write an explicit formula for the sequence.
    \item Find the sum of the first three terms the sequence.
\end{enumerate}

\newpage
AII-F.LE.2: Construct a linear or exponential function symbolically given: a graph, a description of the relationship, or two input-output pairs (include reading these from a table).

\item The graph shows the amount of a medicine $m$, in milligrams, remaining in a patient's body $h$ hours after receiving an injection. The amount of the medicine decreases exponentially.
    \begin{center}
    \begin{tikzpicture}[x=1cm, y=0.15cm, xscale=2.5]
        %\draw [thin, color=lightgray, xstep=0.5cm,ystep=0.75cm] (0,0) grid (3,40);
        \draw [thick, ->] (0,0) -- (+2.8,0) node [below]{$h$};
        \draw [thick, ->] (0,0) -- (0,36) node [left]{$m$};        
        \foreach \x in {0,0.5,...,2.5}
            \draw (\x cm,5pt) -- (\x cm,-5pt) node[below] {$\x$};
        \foreach \y in {0,10,20,...,30}
            \draw[shift={(0,\y)}] (2pt,0pt)--(-2pt,0pt) node[left]{$\y$};
        \draw [thick, ->, smooth,domain=0.:2.4] plot(\x,{32*(0.25^\x)});
        \fill (0,32) ellipse [x radius=1pt, y radius=2.5pt]  node [right] {$(0,32)$};
        \fill (1.5,4) ellipse [x radius=1pt, y radius=2.5pt] node [above right] {$(1.5,4)$};
    \end{tikzpicture}
    \end{center}
    \begin{enumerate}[itemsep=3cm]
        \item By what factor did the medicine decrease in the first hour and a half? Explain how you know.
        \item By what factor did the medicine decrease in the first half hour? What about in the first hour? Explain how you know. \vspace{1cm}
        \item Write an equation relating $m$, the number of milligrams of the drug in the patient’s body, and $h$, the number of hours since the injection.
    \end{enumerate}

\end{enumerate}
\end{document}