\documentclass{beamer}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{venndiagram}

\setlength{\headheight}{26pt}%doesn't seem to fix warning

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

\rhead{\small{19 March 2018}}
\lhead{\small{BECA / Dr. Huson / Mathematics}}

%\vspace{1cm}

\renewcommand{\headrulewidth}{0pt}


\title{Mathematics Class Slides}
\subtitle{Bronx Early College Academy}
\author{Chris Huson}
\date{March 2018}

\begin{document}

\frame{\titlepage}

%\section[Outline]{}
%\frame{\tableofcontents}

\section{12.1 Drui}
\frame
{
  \frametitle{GQ: How do we use the normal curve?}
  \framesubtitle{CCSS: HSS.MD.A.3 Develop a probability distribution for a random variable \qquad \alert{12.1}}

  \begin{block}{Do Now}
    \begin{enumerate}
    \item Confirm the regression equation fit to \#4 p. 348.
    \item How would you interpret the correlation of two variables having $r=-0.65$? (p. 359)
    \item Sketch a normal curve with $X\sim N(500, 100^2)$.
    \href{https://blog.prepscholar.com/sat-standard-deviation}{link}
    \end{enumerate}
 \end{block}
  Homework review\\*
  Lesson:  Regression, residuals, least-squares, extrapolation, mean point $(\bar{x},\bar{y})$ (p. 334-359)\\* 
  Normal distribution, Z-score, inverse normal (p. 538-553) \\%*[5pt]
  Task: The standard normal and Z-score problems, 15H p. 541\\%*[5pt]
  Assessment: Exercise 15H \#1 \& 5 p. 541\\%*[5pt]
  Homework: Problem set regressions, probability distributions
}

\section{11.1 Drui}
\frame
{
  \frametitle{What are the rules for a geometric series?}
  \framesubtitle{CCSS: HSA.SSE.B.4 Geometric series\qquad \alert{11.1}}

  \begin{block}{Do Now: Given the parent function $f(x)=\frac{1}{x}$}
  \begin{enumerate}
      \item Write down the equations of $f$'s asymptotes.
      \item The function $f$ is shifted to the right 3 to make the function $g$. What is the equation for $g(x)$?
      \item $g$ is now shifted up 2 units to make $h$. Find $h(x)$.
  \end{enumerate}
  \end{block}
  Lesson: Geometric sequences \& series formulas. p. 167-179\\*[5pt]
  Task: Example 8 \& 9 (calculator) p. 168-9\\*
  Assessment: Exercise 6D \#1d, e, f\\*
  Homework: Exercise 6E \#1-6 p. 169
}

\frame
{
  \frametitle{Aim and rationale}
  \framesubtitle{There are many important and amazing sequences and series in mathematics.}
  $\displaystyle \frac{1}{2}+\frac{1}{4}+\frac{1}{8}+\frac{1}{16}+\frac{1}{32}+\frac{1}{64} \dots$ Zeno's paradox (Greek)\\*[10pt]  $\displaystyle \frac{1}{2}+\frac{1}{3}+\frac{1}{4}+\frac{1}{5}+\frac{1}{6}+\frac{1}{7} \dots$ harmonic series\\*[10pt]
  $\displaystyle \frac{\pi}{4}=1-\frac{1}{3}+\frac{1}{5}-\frac{1}{7}+\frac{1}{9}-\frac{1}{11}+\frac{1}{13}$ \dots Madhava  (India)\\*[10pt]
  %1, 1, 2, 3, 5, 8, 13, 21, 34, 55, 89,... (Fibonacci)\\*[10pt]
  0.99999999...\\*[10pt]
The aim of this exploration is to discover the patterns, formulas, and rules of geometric series by experimenting and investigating using a spreadsheet to total various example series.\\*[5pt]
  
*Sequence: list of numbers. Series: sum of a sequence of numbers. Geometric sequence: consecutive terms have a constant ratio.
}

\frame
{
  \frametitle{Descriptive statistics terminology}
  \framesubtitle{Make a list of these terms, find their definitions in the textbook.}
  
  Univariate data, bivariate\\*
  Population, sample, random/biased sample, survey, census\\*
  Discrete/continuous data, quantitative/qualitative\\* 
  Central tendency, mean ($\overline{x}, \mu$), median, mode; quartiles, percentiles\\*
  5-figure summary, box \& whisker plots, range, interquartile range, outlier\\*
  Dispersion, standard deviation ($\sigma$), variance ($v=\sigma^2$)\\*
  Frequency distributions (tables/bar charts/histograms)\\*
  Grouped data, class, mid-interval value, boundaries, modal class\\*
  Cumulative frequency distributions

  
}

\frame
{
  \frametitle{Bias and fairness, random variation, \& combinations}
  \framesubtitle{When rolling two dice, why aren't all the possible totals equally likely?}
  Definition:\\*
  A \alert{fair} (p. 67) or \alert{unbiased} (p. 79) process \\*[15pt]
  In mathematics we usually simplify and assume a random process follows exact, idealized probabilities. For example, we assume heads and tails are equally likely results of a coin toss.
  
}

\frame
{
  \frametitle{Bias and fairness, random variation, \& combinations}
  \framesubtitle{When rolling two dice, why aren't all the possible totals equally likely?}
  Definition:\\*
  \alert{Experimental} or \alert{empirical} (p. 65) results \\*[15pt]
  In real life, the results of any experiment have a degree of \alert{random variation}. The observed relative frequencies are estimates of the underlying theoretical probabilities, which grow more accurate with additional trials.
  
}

\frame
{
  \frametitle{Bias and fairness, random variation, \& combinations}
  \framesubtitle{When rolling two dice, why aren't all the possible totals equally likely?}
  Counting events in a \alert{sample space} (p. 78) or calculating \alert{combinations} (p. 184) \\*[15pt]
  The six possible results of rolling a single die are equally likely, $\mathrm P(x)=\frac{1}{6}$, if we assume the die is fair. Similarly, the probability of any of the 36 $(6 \times 6)$ possible results of rolling two dice are equally likely, $\mathrm P(x)=(\frac{1}{6})^2$. However, the probability of a particular total varies according to how many combinations lead to that total. Thus, for example, 7 can be rolled six different ways, so $\mathrm P(7)=\frac{6}{36}$, while 2 can only result one way, $\mathrm P(2)=\frac{1}{36}$.
  
}

\frame
{
  \frametitle{Sets, subsets, \& proper subsets}
  
  Definitions:\\*
  A \alert{set} is an unordered collection of elements.\\ e.g. \{red, white, blue\} (do not repeat elements)\\*[5pt]
  \alert{Subset}: Set $A$ is a subset of set $B$ if and only if all of the elements of $A$ are elements of $B$.\\
  Written: $A \subseteq B$\\[5pt]
  \alert{Proper subset}: $A \subseteq B$ and $A$ is not equal to $B$. Written: $A \subset B$\\[5pt]
  The \alert{empty set} is a subset of all sets. $\{\} \text{ or } \emptyset$
  
}


\frame
{
  \frametitle{GQ: Combinatorics problem}
  \framesubtitle{CCSS: F.IF.B.6 Calculate \& interpret the rate of change of a function}

  \begin{block}{Show the formula and then use your calculator function}
  \begin{enumerate}
      \item You have a \$1 bill, a \$5 bill, a \$10 bill, a \$20 bill, a quarter, a dime, a nickel, and a penny. How many different total amounts can you make by choosing six bills and coins?
  \end{enumerate}
  \end{block}
  What is the number of the set you are choosing from?\\%*[5pt]
  How many are you picking?\\%*[5pt]
  Does their order matter?
}

\begin{frame}{Do Now \#1: Phone preferences by gender}
    \framesubtitle{Given the frequency table, make a Venn diagram}
    \begin{tabular}{l|c|r|}
        & Android & iPhone\\ 
        \hline 
        Boys & 15 & 5 \\ 
        \hline 
        Girls & 5 & 15 \\
        \hline 
    \end{tabular}\\*[10pt]
    \centering
    $A=\{ \text{prefers Android}\}$ and $B=\{ \text{is a boy}\}$
    \begin{venndiagram2sets}[tikzoptions={scale=1.0}]
    \end{venndiagram2sets}
\end{frame}

\begin{frame}{Do Now \#2: Independence}
    \framesubtitle{Given the situation, make a Venn diagram, frequency table, and tree representing}
    $\mathrm{P}(A)=0.6$, $\mathrm{P}(B)=0.5$, $\mathrm{P}(A \cap B)=0.3$
    \centering
    \begin{venndiagram2sets}[tikzoptions={scale=1.0}]
    \end{venndiagram2sets}\\*[10pt]
    \begin{tabular}{l|c|r|}
        & $A$ & $A^\prime$\\ 
        \hline 
        $B$ &  \qquad \qquad &  \qquad \qquad \\ 
        \hline 
        $B^\prime$ &  &  \\
        \hline 
    \end{tabular}\\*[10pt]
\end{frame}

\begin{frame}{$\mathrm P(A \cup B) = \mathrm P(A) + \mathrm P(B) - \mathrm P(A \cap B)$}
    \framesubtitle{The addition rule}
    \begin{venndiagram2sets}[tikzoptions={scale=2}]
    \end{venndiagram2sets}
\end{frame}

\begin{frame}{Distributions}
    \framesubtitle{Tables and charts used to summarize a problem situation}
    A \alert{frequency distribution} displays the number of times each event in the sample space occurs, either in tabular or graphical form.\\*[10pt]
    A \alert{probability distribution} shows the same data, normalizing the totals to one.
\end{frame}


\begin{frame}{Technical writing}
    \framesubtitle{Write a short paper answering the query: \\* "How many subsets can be picked from a group of four students?"}
    \begin{enumerate}
        \item Logical, step-by-step explanation, using an example
        \item Precise terminology, succinct: combination, permutation, order (matters), event, sample space, set, subset, with /without replacement, factorial
        \item Notation: algebra symbols, tables, trees, grids
        \item Summary, big-picture, conceptual idea
        \item Audience: student peers
    \end{enumerate}
\end{frame}





\begin{frame}{Combinatorics formulas}
    \alert{Combinations}, when order doesn't matter
	$$_nC_r = \frac{n!}{(n-r)! r!} \qquad \text{''n pick r"}$$
    \alert{Permutations}, when order does matter
	$$_nP_r = \frac{n!}{(n-r)!} $$
\end{frame}

\begin{frame}{Definition of theoretical probability}
    The \alert{theoretical probability} of an event $A$ is $\displaystyle \mathrm P(A) = \frac{n(A)}{n(U)}$\\*[10pt]
    \quad where $n(A)$ is the number of ways an event can occur\\*[5pt]
    \quad and $n(U)$ is the total number of possible outcomes (p. 65)\\*[10pt]
    Theoretically, in $n$ trials, one would expect the event to occur $n \times \mathrm P(A)$ times\\*[10pt]
    Probabilities are between 0 and 1, inclusive. $0 \leq \mathrm P(X) \leq 1$
\end{frame}

\begin{frame}{Empirical (experimental) probability}
    The \alert{relative frequency} of an event can be used as an estimate of its probability. $$\displaystyle \mathrm P(A) = \frac{\text{number of occurrences of event } A}{\text{total number of trials}}$$
    The larger the number of trials the more reliable the estimate of probability.
\end{frame}

\begin{frame}{Independence and mutual exclusivity}
    Two events are \alert{independent} if the occurrence of one does not affect the probability of the other. $$\displaystyle \mathrm P(\text{both }A \text{ and }B \text{ occur}) = \mathrm P(A) \times \mathrm P(B)$$
    Two events are \alert{mutually exclusive} if they never occur together. 
    $$\displaystyle \mathrm P(\text{both }A \text{ and }B \text{ occur}) = 0 \qquad \text{and}$$
    $$\mathrm P(\text{either }A \text{ or }B \text{ occur}) = \mathrm P(A) + \mathrm P(B)$$
\end{frame}

\begin{frame}{Venn diagrams}
    \framesubtitle{For organizing compound events}
    When two events can occur, and perhaps both, or neither.
    \begin{venndiagram2sets}[tikzoptions={scale=1.5}]
    \end{venndiagram2sets}
\end{frame}

\begin{frame}{The union of sets: $A \cup B$}
    That $A$ happens, or $B$ happens, or both
    \begin{venndiagram2sets}[tikzoptions={scale=1.5}]
    \fillA
    \fillB
    \end{venndiagram2sets}
\end{frame}

\begin{frame}{The intersection of sets: $A \cap B$}
    That both $A$ and $B$ happen
    \begin{venndiagram2sets}[tikzoptions={scale=1.5}]
    \fillACapB
    \end{venndiagram2sets}
\end{frame}

\begin{frame}{The addition rule}
    \framesubtitle{That $A$ or $B$ or both occur}
    
    When two events can occur, and perhaps both
    
    \begin{venndiagram2sets}%[labelA={primes}, labelB={evens}, shade =lightgray]%
    %\fillA
    %\fillB
    %\fillACapB
    \end{venndiagram2sets}

    $$P(\text{either }A \text{ or }B \text{ occur}) = P(A) + P(B) - P(\text{both }A \text{ and }B \text{ occur})$$
\end{frame}

\begin{frame}{Vocabulary for probability \& statistics}
    event, experiment, random\\*[5pt]
    probability, P(A), values [0,1]\\*[5pt]
    theoretical, empirical, subjective\\*[5pt]
    sample space, U; frequency, trials\\*[5pt]
    n(U) = number of possibilities\\*[5pt]
    P(A) = n(A)/n(U); expected = n * P
\end{frame}

\frame
{
  \frametitle{Interpreting a displacement vs time graph}
  \framesubtitle{CCSS: F.IF.B.6 Calculate \& interpret the rate of change of a function}

  \begin{block}{Consider the function $f(x)=-x^2+2x+3$}
  \begin{enumerate}
      \item Factor $f$ and state its zeros.
      \item Restate $f$ in vertex form. Write down the vertex as an ordered pair.
      \item Over what intervals is the function increasing, decreasing, and neither?
      \item If $f(x)$ represents the height of a diver over the domain $0 \leq x \leq 3$, interpret $f(0)$, the vertex, and $f(3)$
      \item What does the "slope" of the curve represent?
  \end{enumerate}
  \end{block}
}


\end{document}
independent events: P(A&B)=P(A)*P(B) 
dependent events, mutually exclusive
P(A or B)= P(A) + P(B) - P(A&B)
P(A) = n(A)/n(U)