\input{preamble}

\fancyhead[LE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{4cm} \,\\}
\fancyhead[LO]{BECA / Dr. Huson / Geometry\\*  Learning Trajectories\\* 2022-2023}

\begin{document}

\subsubsection*{Data Learning Trajectories: Sets and Venn diagrams}
\begin{enumerate}
\item Write each letter in the appropriate location in the Venn diagram.\\[0.25cm]
    \qquad $A = \{a, b, c, d, e\}$
    \qquad $B = \{a, e, i, o, u\}$
    \begin{center}
        \begin{venndiagram2sets}[tikzoptions={scale=1.5}]
        \end{venndiagram2sets}U
    \end{center}
\begin{multicols}{2}
        \begin{enumerate}
        \item What is $A \cup B$?
        \item What is $A \cap B$?
    \end{enumerate}
\end{multicols} \vspace{0.5cm}

\item Given the universal set $U$ is the set of positive integers less than 13. Subsets: \\[0.5cm]
\qquad $A =$ \{integers that are multiples of 3\}\qquad 
\qquad $B =$ \{prime numbers\} \\[0.5cm]
\emph{(Prime numbers have only themselves and one as factors. One is not prime.)}
\begin{enumerate}
    \begin{multicols}{2}

            %\item How many elements are in the universal set $U$?
            \item List the members of $A$
            \item List the members of $B$
    \end{multicols} \vspace{1cm}

    \item Place the elements of $A$ and $B$ in the appropriate regions in the Venn diagram.
    \begin{center}
        \begin{venndiagram2sets}[tikzoptions={scale=2.0}]
        \end{venndiagram2sets}U
        \end{center}

        \item List the set $A \cap B$
    \end{enumerate}

\newpage
\item Complete the Venn diagram with the colors of the flags of America ($A$), Italy ($B$), and China ($C$).
    \begin{center}
      \begin{venndiagram3sets}[tikzoptions={scale=1.7}]
      \end{venndiagram3sets}U
    \end{center}

\item Suppose there are 19 species of fruit-eating monkeys in the western hemisphere. Their diets are as follows:
\begin{itemize}
  \item 16 species of monkeys eat bananas
  \item 12 species eat apples
  \item 11 eat both apples and bananas
\end{itemize}
Complete the Venn diagram below, writing the number of species of fruit-eating monkeys in each region to represent the situation. (Use ``A" for apple, ``B" for banana)
  \begin{center}
    \begin{venndiagram2sets}[tikzoptions={scale=1.5}]
    \end{venndiagram2sets}U
  \end{center}
How many species have a diet that does not include apples nor bananas?

\newpage
\subsubsection*{Challenge}
\item There are 90 juniors at a school taking courses as follows:
\begin{itemize}
  \item 27 are taking Algebra
  \item 35 are taking Botany
  \item 51 are taking Chemistry
  \item 11 are taking Algebra and Chemistry
  \item 6 are taking Algebra and Botany
  \item 13 are taking Botany and Chemistry
  \item 4 are taking all three subjects
\end{itemize}
Complete the Venn diagram below with the number of students in each region to represent the situation.
  \begin{center}
    \begin{venndiagram3sets}[tikzoptions={scale=2}]
    \end{venndiagram3sets}U
  \end{center}
How many juniors are taking none of the three courses?

\end{enumerate}
\end{document}
