\documentclass[12pt, twoside]{article}
\usepackage[letterpaper, margin=1in, headsep=0.5in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{quotes, angles}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{hyperref}

\newif\ifmeta
\metatrue %print standards and topics tags

\title{IB Mathematics}
\author{Chris Huson}
\date{September 2021}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % disable the underline of the header
\raggedbottom


\fancyhead[LE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{4cm} \,\\}
\fancyhead[LO]{BECA / IB Math 01-Linear functions\\* 21 January 2022}

\begin{document}

\subsubsection*{Exam: Linear functions and arithmetic sequences}
Simple interest: $I=Crt$
\begin{enumerate}

\item The rate on a credit card is $15\%$ per annum. Find the interest due on a \$900 purchase after one month. \vspace{3cm}

\item Elizabeth takes out a 6 month loan to purchase and repair a used car for resale. The principal amount is 11,000 British pounds and interest rate is $6.45\%$ per annum. Find the interest Elizabeth pays.
\vspace{4cm}

\item The weight of a turkey $w$ in kilograms over a period of time $t$ measured in months is shown in the table.
\begin{enumerate}
  \item Plot the data as points on the grid.
  \item Draw a line of best fit on the graph. Use a straight edge for full credit.
\end{enumerate}
  \begin{center} 
  \begin{tikzpicture}[scale=0.8]
    \draw [help lines] (-0.25,-0.25) grid (8,8);
    \draw [thick, ->] (-0.2,0) -- (8.4,0) node [below right] {$t$};
    \draw [thick, ->] (0,-0.2)--(0,8.4) node [right] {$w$};
    \foreach \x in {1,2,...,8} \draw (\x cm,1pt) -- (\x cm,-1pt) node[anchor=north] {$\x$};
    \foreach \y in {1,2,...,8} \draw (1pt,\y cm) -- (-1pt,\y cm) node[anchor=east] {$\y$};

    \draw [thick] (-7,-0.5) -- (-7,8);
    \draw [thick] (-8.5,7) -- (-5.5,7);
    \node at (-8,7.5){$t$}; \node at (-6,7.5){$w$};
    \node at (-8,6){$1$}; \node at (-6,6){$4$};
    \node at (-8,4.5){$3$}; \node at (-6,4.5){$5$};
    \node at (-8,3){$4$}; \node at (-6,3){$5$};
    \node at (-8,1.5){$6$}; \node at (-6,1.5){$6$};
    \node at (-8,0){$7$}; \node at (-6,0){$7$};
  \end{tikzpicture}
  \end{center}

\newpage
Arithmetic sequences\\[0.25cm]
Terms: $u_n=u_1 + d(n-1)$\\[0.25cm]
Sum: $\displaystyle S_n= \frac{n}{2}(u_1 + u_n)$\\[0.25cm]


\item Given the arithmetic sequence $3,7,11,15,19, \dots$ \hfill [6]
  \begin{enumerate}[itemsep=1cm]
    \item Find the common difference $d$.
    \item Write down the next term, $u_6$.
    \item Find the twelfth term.\vspace{1cm}
    \item Find the sum of the first twelve terms.
  \end{enumerate} \vspace{2cm}

\item In an arithmetic sequence the first term is 7 and the fourth term is 25. \hfill [6]
  \begin{enumerate}[itemsep=2cm]
    \item Find the common difference $d$.
    \item Find the tenth term, $u_{10}$.\vspace{1cm}
    \item Find the sum of the first ten terms.
  \end{enumerate} \vspace{3cm}

\newpage
\item The second term of an arithmetic sequence is 19 and the sixth term is 7. \hfill [6]
  \begin{enumerate}[itemsep=3cm]
    \item Find the common difference $d$.
    \item Find the first term, $u_{1}$.
    \item Find the sum of the first six terms.
  \end{enumerate} \vspace{2cm}

\item Given $f(x)=\frac{3}{5}x-3$.  \hfill [3]
\begin{enumerate}
  \item Find $f(10)$. \vspace{2cm}
  \item Find$f^{-1}(0)$.
\end{enumerate} \vspace{4cm}

\newpage
\item A function is defined over the domain $0 \leq x \leq 700$. Its intercepts are $(700,0)$ and $(0, 80)$. Draw the function on the grid. Label and number the $x$- and $y$-axes with an appropriate scale. \hfill [3]
  \begin{center}
  \begin{tikzpicture}[scale=1]
    %\draw [help lines] (-3,-2) grid (4,6);
    \draw [thick, ->] (-1.2,0) -- (10.4,0) node [below right] {$x$};
    \draw [thick, ->] (0,-1.2)--(0,10.5) node [right] {$y$};
    \foreach \x in {-1, 1,2, ..., 10} \draw (\x cm,4pt) -- (\x cm,-4pt);% node[anchor=north] {$\x$};
    \foreach \y in {1,2,..., 10} \draw (2pt,\y cm) -- (-2pt,\y cm);% node[anchor=east] {$\y$};
    %\fill (3,3) circle[radius=0.1] node[above right]{$(3,3)$};
    %\fill (6,-1) circle[radius=0.1] node[below left]{$(6,-1)$};
    %\draw [thick, <->,smooth,samples=20,domain=2.5:6.5] plot(\x,-1.33*\x+7);
  \end{tikzpicture}
  \end{center}
  
\end{enumerate}
\end{document}