\documentclass{beamer}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{venndiagram}

%\usepackage{pgfplots}
%\pgfplotsset{width=10cm,compat=1.9}
%\usepackage{pgfplotstable}

\setlength{\headheight}{26pt}%doesn't seem to fix warning

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

%\rhead{\small{5 September 2018}}
\lhead{\small{BECA / Dr. Huson / 11.1 IB Math Unit 1}}

\renewcommand{\headrulewidth}{0pt}

\title{Mathematics Class Slides}
\subtitle{Bronx Early College Academy}
\author{Chris Huson}
\date{13-17 September 2021}

\begin{document}
\frame{\titlepage}
\section[Outline]{}
\frame{\tableofcontents}


\section{1.1 1st day of Geometry, Segment addition, 13 Sept}
\frame
{
  \frametitle{Learning Target: I can measure and diagram my world}
  \framesubtitle{CCSS: HSG.CO.A.1 Know precise geometric definitions \hfill \alert{1.1 Monday 13 Sept}}

  Welcome back to school
  \begin{block}{Do Now: Measurement}
  \begin{enumerate}
      \item Notebook first page: Name / Course / Instructor
      \item Diagram people closest to you and their distance
      \item Early finishers: Calculate diagonal distances
  \end{enumerate}
  \end{block}
  Supply list: Composition book, looseleaf, pencils \& pens, \\*
  compass and ruler; Optional: calculator, folder \\[0.25cm]
  Lesson: Linear functions, slope, solving; vertical line test p 4-6 \\[0.25cm]
  Homework: Diagram your bedroom (with measurements), or another room
}

%Prepare copies of formula sheets

  \section{1.2 Function domain and range}
  \frame
  {
    \frametitle{Learning Target: I can apply domain and range}
    \framesubtitle{CCSS: HSF.IF.C.7 Analyze functions \hfill \alert{1.2 Tuesday 14 Sept}}

    \begin{block}{Do Now: In your notebook}
    \begin{enumerate}
      \item Solve for $x$: \\
      \hspace{1cm} $x-7=11$ \hspace{1cm}  $2(x-5) \geq 4$
      \item What is the slope of the line $y=3x-2$?
      \item $f(x) = x^2 - 3$. Find $f(1)$
    \end{enumerate}
    \end{block}
    Lesson: Domain, range, function review pp 204-8\\[5pt]
    Groupwork: Investigation 1 pp 206-8\\[5pt]
    Homework: Skills Check p 205
  }

  \section{1.3 Precision and significant figures, 9 Sept}
  \frame
  {
    \frametitle{Learning Target: What is the appropriate precision for a calculation?}
    \framesubtitle{CCSS: MP5 Attend to precision \hfill \alert{1.3 Monday 9 Sept}}

    \begin{block}{Do Now: Textbook chapter warmup, use looseleaf paper}
    \begin{enumerate}
        \item Skills check \#1-3 p. 3
    \end{enumerate}
    \end{block}
    Lesson: Rounding, significant figures, error bars pp. 1-5\\
    Exercise 1A, \#1-2, p. 5
    \\[0.5cm]
    Homework: Calculation and rounding practice
  }

  \section{1.4 Error bounds, 10 Sept}
  \frame
  {
    \frametitle{Learning Target: How do we measure the bounds of errors?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.4 Tuesday 10 Sept}}

    \begin{block}{Do Now: Calculator practice}
    \begin{enumerate}
        \item Chapter review \#1 p. 39
        \item Pay careful attention to saving calculator values, rather than copying to paper and reentering.
        \item Check your answers in back of book, p. 766
    \end{enumerate}
    \end{block}
    Lesson: Bounds and errors pp. 6-8\\ \bigskip
    Practice exercises 1B p. 8-9\\
    Homework: Function substitution, domain and range
  }

  \section{1.5 Exponents \& scientific notation, 11 Sept}
  \frame
  {
    \frametitle{Learning Target: How do we write very large or small numbers?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.5 Wednesday 11 Sept}}

    \begin{block}{Do Now: Precision practice}
    \begin{enumerate}
        \item Practice exercises 1B p. 8-9
        \item Pay careful attention to saving calculator values, rather than copying to paper and reentering.
        \item Check your answers in back of book, p. 765
    \end{enumerate}
    \end{block}
    Lesson: Exponents \& scientific notation pp. 9-12\\ \smallskip
    Note exponent rules top of page 11\\ \smallskip
    Homework: Practice exercises 1C p. 12-13
  }


  \section{1.6 Right triangle trigonometry, 12 Sept}
  \frame
  {
    \frametitle{Learning Target: How do we calculate the side lengths of a right triangle?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.6 Thursday 11 Sept}}

    \begin{block}{Do Now: Precision practice}
    \begin{enumerate}
        \item Chapter review \#2 p. 39
        \item Which will be easier to use, scientific notation or the fully expanded number?
        \item Use proper notation to display your answer clearly
    \end{enumerate}
    \end{block}
    Homework review \\
    Lesson: Right triangle trigonometry pp. 13-15\\ \smallskip
    Angle of elevation and depression page 11\\ \smallskip
    Homework: Practice exercises 1D p. 16-17
  }


  \section{1.7 Sine rule, 13 Sept}
  \frame
  {
    \frametitle{GQ: How do we calculate the side lengths of a non-right triangle?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.7 Friday 13 Sept}}

    \begin{block}{Do Now: Precision practice}
    \begin{enumerate}
        \item Chapter review \#3 p. 39
        \item Learn how to use the calculator to solve an equation. (multiple methods)
    \end{enumerate}
    \end{block}
    Lesson: Non-right triangles and the sine rule pp. 17-21\\ \smallskip
    The ambiguous case page 21\\ \smallskip
    Homework: Practice exercises 1E p. 21-22
  }

  \section{1.8 Sine formula for the area of a triangle, 16 Sept}
  \frame
  {
    \frametitle{GQ: How do we calculate the area of a triangle?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.8 Monday 16 Sept}}

    \begin{block}{Do Now: Precision practice}
    \begin{enumerate}
        \item Chapter review \#4b p. 39
        \item Note that both $\displaystyle \frac{15}{\sin 31}=\frac{13.4}{\sin R}$ and $\displaystyle \frac{\sin 31}{15}=\frac{\sin R}{13.4}$. \\ \bigskip
        Which is easier to solve?
    \end{enumerate}
    \end{block}
    Lesson: Practicing applying the sine rule pp. 17-21\\
    The ambiguous case page 21\\
    The sine formula for the area of a triangle page 22\\ \smallskip
    Homework: Practice exercises 1E p. 21-22
  }

  \section{1.9 Deltamath: scientific notation, trig 17 Sept}
  \frame
  {
    \frametitle{GQ: How do we practice the law of sines?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.9 Tuesday 17 Sept}}

    \begin{block}{Deltamath practice: scientific notation, trig}
      \begin{enumerate}
        \item Laptops, login with Teacher ID \alert{546068}
        \item Do Deltamath sections in order \\
        Practice comes first, then new topics
        \item Work extra problems on the skills you need to practice
    \end{enumerate}
    \end{block}
    New material: The sine formula for the area of a triangle page 22\\
    Radian / degree conversion; law of cosines\\ \smallskip
    Homework: Complete Deltamath problems, 10:00PM deadline
  }

  \section{1.10 Cosine rule, 18 Sept}
  \frame
  {
    \frametitle{GQ: How do we calculate the angles of a triangle?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.10 Wednesday 18 Sept}}

    \begin{block}{Do Now: Precision practice}
    \begin{enumerate}
        \item Chapter review \#6 p. 39
    \end{enumerate}
    \end{block}
    Lesson: The cosine rule pp. 23-24\\
    The sine formula for the area of a triangle page 22\\ \smallskip
    Homework: Practice exercises 1F p. 24-25
  }


  \section{1.11 Sine \& cosine rule practice, 19 Sept}
  \frame
  {
    \frametitle{GQ: How do we ``solve" a triangle?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.11 Thursday 19 Sept}}

    \begin{block}{Do Now: IB exam problems}
    \begin{enumerate}
        \item Applications of the sine and cosine rules
    \end{enumerate}
    \end{block}
    Lesson: The cosine rule pp. 23-24\\
    The sine formula for the area of a triangle page 22\\ \smallskip
    Homework: Study Arc length and area of sector \\
    Oxford textbook pp. 25-27 \\
    Deltamath, practice circle sectors and arc length \\
    Khan Academy, log in and use videos as resource (DrHuson)
  }

  \section{1.12 Circle sectors \& arc length, 20 Sept}
  \frame
  {
    \frametitle{GQ: How do we calculate the angles of a triangle?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.12 Friday 20 Sept}}

    Continue IB exam trig problems \\ \bigskip
    Lesson: The cosine rule pp. 23-24\\
    The sine formula for the area of a triangle page 22\\ \smallskip
    Homework: Complete Khan videos and Deltamath problems if you haven't already. \\
    Practice exercises 1G p. 26-27
  }

  \section{1.13 3-dimensional figures, volume, 23 Sept}
  \frame
  {
    \frametitle{GQ: How do we calculate the volumes of objects?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.13 Monday 23 Sept}}

    \begin{block}{Do Now: Developing inquiry skills, top of page 28}
      \begin{enumerate}
          \item Draw a scale model of the surveying of Mt. Everest on IB centimeter graph paper. (use a protractor)
          \item Determine the height of the mountain by measuring your model
          \item Calculate the height using trig formulas
      \end{enumerate}
      \end{block}
  
    Continue IB exam trig problems \\ \bigskip
    Lesson: Solid geometry terminology, volume formulas\\ \smallskip
    Homework: Practice exercises 1H p. 30-31 \\
    Khan videos and Deltamath problems
  }

  \section{1.14 3-dimensional figures, surface area, nets, 24 Sept}
  \frame
  {
    \frametitle{GQ: How do we calculate the volumes of objects?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.14 Tuesday 24 Sept}}

    \begin{block}{Do Now: Calculate the volume of each object}
      \begin{enumerate}
          \item A sphere with a radius of 15 cm
          \item A circular pond 40 meters in diameter with a depth of 20 centimeters
          \item A cone with a height of 2 feet and diameter of 20 inches
          \item Find the radius of a sphere with volume $215 \pi$
      \end{enumerate}
      \end{block}
    Lesson: Solid geometry surface area, nets\\ \smallskip
    Investigation 7, page 32 \\ \bigskip
    Homework: Practice exercises 1I p. 35-36
  }

  \section{1.15 3-dimensional figures, internal angles, 25 Sept}
  \frame
  {
    \frametitle{GQ: How do we calculate the slant angles and lengths?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.15 Wednesday 25 Sept}}

    \begin{block}{Do Now: Calculate the surface area of each object}
      \begin{enumerate}
          \item A cylinder 4 cm in diameter with a height of 5 millimeters
          \item A sphere with a radius of 15 cm
          \item A pyramid with a height of 40 feet and base 50 feet by 50 feet
          \item Find the radius of a sphere with surface area $72 \pi$
      \end{enumerate}
      \end{block}
    Lesson: Solid geometry slant angles and lengths\\ \smallskip
    Investigation 7, page 32 \\ \bigskip
    Homework: Return and complete exercises 1E p. 21-22
  }

  \section{1.16 3-dimensional figures, internal angles, 26 Sept}
  \frame
  {
    \frametitle{GQ: How do we calculate the slant angles and lengths?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.16 Thursday 26 Sept}}

    \begin{block}{Do Now: Calculate the surface area of a cone}
      \begin{enumerate}
          \item Developing inquiry skills p. 38 (Mt. Everest)
          \item What formula would apply?
       \end{enumerate}
      \end{block}
    Lesson: Solid geometry, Chapter Summary\\ \smallskip
    Homework: Chapter review 1-10 p. 39-40 (revisit problems)
  }


  \section{1.17 review, bounds, 27 Sept}
  \frame
  {
    \frametitle{GQ: How do we calculate the bounds around a value?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.17 Friday 27 Sept}}

    \begin{block}{Do Now Quiz: \href{https://www.smartbmicalculator.com/}{Calculate Body Mass Index} (link)}
      BMI is a measure of a healthy personal weight, $\displaystyle BMI = \frac{w}{h^2}$ \\ \smallskip
      $w$ is a person's weight in kilograms and $h$ is height in meters
      \begin{enumerate} 
          \item Given a height of 170 cm and weight of 77 kg, find the BMI
          \item These measurements are not exact. Assuming the height is between 169-171 cm and weight 76-78 kg, find the bounds of the BMI.
       \end{enumerate}
      \end{block}
    Lesson: Solid geometry, Chapter Summary\\ \smallskip
    Homework: Chapter review 11-17 p. 39-40 (revisit problems)
  }

  \frame
  {
    \frametitle{GQ: How do we calculate the bounds around a value?}
    \framesubtitle{CCSS: MP5 attend to precision}

    \begin{block}{Solution to Do Now Quiz: Calculate Body Mass Index 
      \alert{(7)}}
      \begin{enumerate} 
          \item $\displaystyle BMI = \frac{77}{1.70^2}$ 
          \hspace{3cm} \alert{M1 A1 allow $170^2$}\\ \smallskip
            \hspace{0.8cm} $=26.64359 \dots$ \\
          \hspace{0.8cm} $\approx 26.6$ 
            \hspace{3.2cm} \alert{A1 (N2))}
          \item Lowerbound: $\displaystyle BMI = \frac{76}{1.71^2}$ 
          \hspace{0.8cm} \alert{M1 A1} \\ \smallskip
          \hspace{0.8cm} $=25.9909 \dots$ \\
          \hspace{0.8cm} $\approx 26.0$  \\ \smallskip
          Upperbound: $\displaystyle BMI = \frac{78}{1.69^2}$ \\ \smallskip
          \hspace{0.8cm} $=27.30996 \dots$ \\
          \hspace{0.8cm} $\approx 27.3$  \hspace{3cm} \alert{A1 A1 (N3)} \\
          \hspace{4cm} \alert{award M1 A1 f.t. for 26.6, 26.7}
       \end{enumerate}
      \end{block}
    Proper header with full name, date, and title (5 percentage points)
    
  }

  \frame
  {
    \frametitle{GQ: How do we calculate the bounds around a value?}
    \framesubtitle{CCSS: MP5 attend to precision}

    \begin{block}{Quiz Corrections: Calculate Body Mass Index 
      \alert{required}}
      \begin{itemize} 
          \item Proper header with full name, date, and title
          \item Work downward in single column on left, in pen 
            \\(you can add notes and diagrams on the right)
          \item Skip a line and number the problem
          \item Label to the left of equals sign (e.g. $BMI=$)
          \item Show substitution step
          \item Write the full calculator display (with ellipse)
          \item Show the rounded value, 3 sig-figs (exact value is also ok)
       \end{itemize}
      \end{block}
    Copy this checklist into your notebook
    
  }

  \section{1.18 review, trig, 2 October}
  \frame
  {
    \frametitle{GQ: How do we apply trig rules to situations?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.18 Wednesday 2 October}}

    \begin{block}{Do Now: Classwork handout \#1}
      \begin{itemize}
          \item The area of a triangle
          \item The cosine rule 
          \item The sine rule, including the ambiguous case
       \end{itemize}
      \end{block}
    Lesson: Circle sector situations\\ \smallskip
    Homework: Complete handout. (revisit Chapter review 1-17 p. 38-40)
  }

  \section{1.19 review, trig, 3 October}
  \frame
  {
    \frametitle{GQ: How do we apply trig rules to situations?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.19 Thursday 3 October}}

    \begin{block}{Do Now: Classwork handout \#1}
      \begin{itemize}
          \item The area of a triangle
          \item The cosine rule 
          \item The sine rule, including the ambiguous case
       \end{itemize}
      \end{block}
    Lesson: Circle sector situations\\ \smallskip
    Homework: Complete handout. (revisit Chapter review 1-17 p. 38-40)
  }

  \section{1.20 test review, trig, 7 October}
  \frame
  {
    \frametitle{GQ: How do we apply trig rules to situations?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.20 Monday 7 October}}

    \begin{block}{Do Now: Review exit note quiz 1.16}
      \begin{itemize}
          \item Using the law of sines to solve a triangle
          \item The Pythagorean theorem and slant height 
          \item The area of a triangle, including the ambiguous case
       \end{itemize}
      \end{block}
    Lesson: Review bounds, rounding (BMI quiz)\\ \smallskip
    \hspace{2cm} Review trig law of sines, cosines, triangle area\\ \smallskip
    Homework: Pretest \alert{(unit exam tomorrow)}
  }

  \section{1.21 unit test Trigonometry, marking period end, 8 October}
  \frame
  {
    \frametitle{GQ: How do we apply trig rules to situations?}
    \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{1.21 Tuesday 8 October}}

    \begin{block}{Unit Exam}
      \begin{itemize}
          \item Bounds of approximation, rounding (BMI application)
          \item Using the law of cosines to find a $\triangle$ length or angle
          \item Using the law of sines to solve a triangle
          \item The area of a triangle, including the ambiguous case
          \item The Pythagorean theorem and slant height 
       \end{itemize}
      \end{block}
    Homework: Statistics concepts
  }

\end{document}
