\documentclass[12pt, oneside]{article}
\usepackage[letterpaper, margin=1in, headsep=0.5in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{quotes, angles}
\usepackage{graphicx}
%\usepackage{pgfplots}
%\pgfplotsset{width=10cm,compat=1.9}
%\usepgfplotslibrary{statistics}
%\usepackage{pgfplotstable}
%\usepackage{tkz-fct}
%\usepackage{venndiagram}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage \\Name: \hspace{1.5in}.\\}
\lhead{BECA / Dr. Huson / 12.1 IB Math SL\\4 October 2018}

\renewcommand{\headrulewidth}{0pt}

\begin{document}
\subsubsection*{Unit 1 Test: Introduction to differential calculus}
Show working for all problems. State answers exactly or to three significant figures.
  \vspace{0.5cm}
  \begin{enumerate}

  \item Find the derivative of each function.
  \begin{itemize}
    \item[(a)] $f(x) = x^2 + 3x + 4$
  	\item[(b)] $g(x)=\frac{1}{6}x^3-\ln x$
  	\item[(c)] $h(x)=e^x \sin x$
  	\item[(d)] $\displaystyle j(x)= \frac{3e^x}{x^2}$
  \end{itemize}

  \item Find $f'(x)$  for the following function. Express your final result without negative exponents.
  	 \[	f(x) = \frac{x^3-4x-8}{x}\]

  \item	Sketch the function $f(x) = x^2 - 4x - 5$.
  \begin{itemize}
      \item[(a)] Find $f(1)$.
  	\item[(b)] Find $f'(x)$.
  	\item[(c)] What is the slope of a tangent to $f$ when $x=1$?
  	\item[(d)] What is the equation of the line tangent to $f$ when $x=1$?
  	\item[(e)] What is the equation of the line normal to $f$ when $x=1$?
  	\item[(e)] Add the tangent and normal lines to the sketch, labeling the point of tangency as a coordinate pair.
  \end{itemize}

%  \item Find the equation of the tangent to $\displaystyle f(x) = \frac{4}{x^2}$ when $x = 1$.

  \item	A function is given as $y = ax^2 + bx + 6$.
  \begin{itemize}
      \item[(a)] Find $\displaystyle \frac {dy}{dx}$.
  	\item[(b)] If the gradient of this function is 2 when $x$ is 6, write an equation in terms of $a$ and $b$.
  	\item[(c)] If the point $(3, -15)$ lies on the graph of the function find a second equation in terms of $a$ and $b$.
  	\item[(d)] Spicy: Solve for $x$ in terms of $a$ and $b$ when
  	$\displaystyle \frac {dy}{dx}=0$. \\[10pt]
  	Where have you seen this expression before? Explain the connection.
  \end{itemize}

  \item Spicy: Show that the derivative of $f(x)=x^2+1$ is $f'(x)=2x$ from first principles using the definition of the derivative as a limit.

\end{enumerate}

\end{document}





\item Consider the function $f(x) = x^3 - 4x^2 - 3x + 18$.
\begin{itemize}
    \item[(a)] Find $\displaystyle \frac {dy}{dx}$.
	\item[(b)] Find the values of $f(x)$ for $a$ and $b$ in the table below:\\
	\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
	\hline
	$x$ & -3 & -2 & -1 & 0 & 1 & 2 & 3 & 4 & 5\\
	\hline
    $f(x)$ & -36 & $a$ & 16 & $b$ & 12 & 4 & 0 & 6 & 28\\
	\hline
	\end{tabular}
	\item[(c)] Using a scale of 1 cm for each unit on the $x$-axis and 1 cm for each 5 units on the $y$-axis, draw the graph of $f(x)$ for $-3 \leq x \leq 5$. Label it clearly using IB conventions.
	\item[(d)] The gradient of the curve at any particular point varies. Within the interval $-3 \leq x \leq 5$, state all the intervals over which the gradient of the curve is
    \begin{itemize}
    \item[(i)] Negative
    \item[(ii)] Positive
    \end{itemize}

\end{itemize}
