\documentclass{beamer}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{venndiagram}

%\usepackage{pgfplots}
%\pgfplotsset{width=10cm,compat=1.9}
%\usepackage{pgfplotstable}

\setlength{\headheight}{26pt}%doesn't seem to fix warning

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

%\rhead{\small{5 September 2018}}
\lhead{\small{BECA / Dr. Huson / IB Math Unit 2}}

\renewcommand{\headrulewidth}{0pt}

\title{Mathematics Class Slides}
\subtitle{Bronx Early College Academy}
\author{Chris Huson}
\date{15 October 2019}

\begin{document}
\frame{\titlepage}
\section[Outline]{}
\frame{\tableofcontents}

\section{3.0 Exploration project paper schedule}
\frame
{
  \frametitle{GQ: How do we employ mathematics to explore a topic?}
  \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{originally Thursday 31 Oct}}
  \begin{block}{Exploration: Schedule and deadlines}
    \begin{enumerate}
      \item Topic selection - Monday November 4th
      \begin{enumerate}
        \item Independent work on introduction, data, mathematics - Nov 11
        \item Complete design of methods, collect data - Nov 15
      \end{enumerate}
      \item Complete paper for peer review - Friday November 22nd
      \item Complete paper for grade - Friday December 6th
      \item Final paper - Friday January 17th
    \end{enumerate}
    \end{block}
}

\section{3.1 Exploration paper student work time (1) 12 Nov}
\frame
{
  \frametitle{GQ: How do we use mathematics to explore a topic?}
  \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{3.1 Tuesday 12 Nov}}

  \begin{block}{Work on exploration papers}
  \begin{enumerate}
      \item Inputs: what data will you use and how will you get it? 
      \item What mathematics will you apply (find the textbook chapter)
      \item Outputs: What results will you use to answer your aim?
      \item Start drafting and re-drafting your introduction (aim, rationale, personal engagement)
  \end{enumerate}
  \end{block}
  Homework: Develop exploration 
}

\section{3.2 Introduction to probability and discrete variables 13 Nov}
\frame
{
  \frametitle{GQ: How do we use mathematics to explore a topic?}
  \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{3.2 Wednesday 13 Nov}}

  \begin{block}{Do Now Skills check page 571}
  \begin{enumerate}
      \item Calculator for the mean value; answer using correct notation 
      \item Note the calculator graping example to the left
  \end{enumerate}
  \end{block}
  Afterschool today; parent conferences tomorrow 4:00-7:00, Friday\\
  Lesson: discrete random variables and their probabilities, notation
  Grouping continuous data page 656\\
  Homework: Read and evaluate sample exploration paper according to criteria pp. 737-740
}

\section{3.3 Probability distributions and expected value 14 Nov}
\frame
{
  \frametitle{GQ: How do we quantify the distribution of a random variable?}
  \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{3.3 Thursday 14 Nov}}

  \begin{block}{2.16 Do Now: Dice probability}
  \begin{enumerate}
      \item probability tables (pdf)
  \end{enumerate}
  \end{block}
  Lesson: Probability distributions and expected value\\ 
  Calculator use to calculate pdfs and cdfs \\ \smallskip
  Homework: Textbook exercises 13A \#1-2, p. 579; exploration paper
}

\section{3.4 Exploration paper student work time (2) 15 Nov}
\frame
{
  \frametitle{GQ: How do we use mathematics to explore a topic?}
  \framesubtitle{CCSS: MP5 attend to precision \hfill \alert{3.4 Friday 15 Nov}}

  \begin{block}{Work on exploration papers}
  \begin{enumerate}
      \item Inputs: what data will you use and how will you get it? 
      \item What mathematics will you apply (find the textbook chapter)
      \item Outputs: What results will you use to answer your aim?
      \item Start drafting and re-drafting your introduction (aim, rationale, personal engagement)
  \end{enumerate}
  \end{block}
  Homework: Develop exploration 
}
\end{document}

Friday: Desmos graphing of soccer shot angle optimization project 

https://www.economist.com/graphic-detail/2019/10/25/how-being-second-choice-could-put-elizabeth-warren-on-top?cid1=cust/dailypicks1/n/bl/n/20191028n/owned/n/n/dailypicks1/n/n/NA/333375/n