\documentclass[12pt, twoside]{article}
\input{../preamble}

\fancyhead[LE]{\thepage}
\fancyhead[RO]{\thepage \\ Name: \hspace{4cm} \,\\}
\fancyhead[LO]{BECA / Dr. Huson / Geometry\\*  Unit 8: Year-to-date Regents review\\* 6 May 2025}

\begin{document}

\subsubsection*{8.4 Quiz: Area, volume, density, solids}
\begin{enumerate}
\item Find the volume of a rectangular prism with length 8 cm, width 10 cm, and height 7.5 cm. \vspace{3cm}

\item A child's tent can be modeled as a pyramid with a square base whose sides measure 48 inches and whose height measures 72 inches. What is the volume of the tent in cubic inches and in cubic feet? \vspace{5cm}

\item Lou has a solid clay brick in the shape of a rectangular prism with a length of 8 inches, a width of 3.5 inches, and a height of 2.25 inches. If the clay weighs 1.055 oz/in$^3$, how much does Lou's brick weigh, to the nearest ounce? \vspace{4cm}


\newpage
\subsubsection*{8.4 Prequiz Regents Practice: 3-D rotation}
\item If a rectangle is continuously rotated around one of its sides, what is the three-dimensional figure formed?
  \begin{multicols}{2}
  \begin{enumerate}
    \item cone
    \item sphere
    \item cylinder
    \item rectangular prism
  \end{enumerate}
\end{multicols}

\item An isosceles right triangle whose legs measure 6 is continuously rotated about one of its legs to form a three-dimensional object. The three-dimensional object is a
\begin{multicols}{2}
    \begin{enumerate}
    \item cylinder with a diameter of 6
    \item cylinder with a diameter of 12
    \item cone with a diameter of 6
    \item cone with a diameter of 12
  \end{enumerate}
\end{multicols}

\item Which three-dimensional figure will result when a rectangle 6 inches long and 5 inches wide is continuously rotated about the longer side?
  \begin{enumerate}
    \item a rectangular prism with a length 6 inches, width 6 inches, and height 5 inches
    \item a rectangular prism with a length 6 inches, width 5 inches, and height 5 inches
    \item a cylinder with a radius of 5 inches and a height of 6 inches
    \item a cylinder with a radius of 6 inches and a height of 5 inches
  \end{enumerate}
  
\item Circle $O$ is centered at the origin. In the diagram below, a quarter of circle $O$ is graphed.
  \begin{center}
    \begin{tikzpicture}[scale=0.6]
      %\draw [help lines] (-4,-4) grid (4,4);
      \draw [thick, <->] (-4,0) -- (4,0) node [below right] {$x$};
      \draw [thick, <->] (0,-3)--(0,2) node [left] {$y$};
      %\draw (0,0) circle [radius=2];
      \draw [thick] (-2,0) arc (180:270:2);
      \node at (0,0) [above right]{$O$};
    \end{tikzpicture}
    \end{center}
  Which three-dimensional figure is generated when the quarter circle is continuously rotated about the $y$-axis?
  \begin{multicols}{2}
    \begin{enumerate}
    \item cone
    \item sphere
    \item cylinder
    \item hemisphere
    \end{enumerate}
  \end{multicols}

\item If an equilateral triangle is continuously rotated around one of its medians, which 3-dimensional object is generated?
\begin{multicols}{2}
      \begin{enumerate}
      \item cone
      \item sphere
      \item pyramid
      \item prism
    \end{enumerate}
  \end{multicols}

\end{enumerate}
\end{document}

